\documentclass[english,man]{apa6}

\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}

% Table formatting
\usepackage{longtable, booktabs}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}

\newenvironment{lltable}
  {\begin{landscape}\begin{center}\begin{ThreePartTable}}
  {\end{ThreePartTable}\end{center}\end{landscape}}

  \usepackage{ifthen} % Only add declarations when endfloat package is loaded
  \ifthenelse{\equal{\string man}{\string man}}{%
   \DeclareDelayedFloatFlavor{ThreePartTable}{table} % Make endfloat play with longtable
   % \DeclareDelayedFloatFlavor{ltable}{table} % Make endfloat play with lscape
   \DeclareDelayedFloatFlavor{lltable}{table} % Make endfloat play with lscape & longtable
  }{}%



% The following enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand\getlongtablewidth{%
 \begingroup
  \ifcsname LT@\roman{LT@tables}\endcsname
  \global\longtablewidth=0pt
  \renewcommand\LT@entry[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}%
  \@nameuse{LT@\roman{LT@tables}}%
  \fi
\endgroup}


\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            pdfauthor={},
            pdftitle={A Validation of the Moral Foundations Questionnaire and Dictionary},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setlength{\parindent}{0pt}
%\setlength{\parskip}{0pt plus 0pt minus 0pt}

\setlength{\emergencystretch}{3em}  % prevent overfull lines

\ifxetex
  \usepackage{polyglossia}
  \setmainlanguage{}
\else
  \usepackage[english]{babel}
\fi

% Manuscript styling
\captionsetup{font=singlespacing,justification=justified}
\usepackage{csquotes}
\usepackage{upgreek}

 % Line numbering
  \usepackage{lineno}
  \linenumbers


\usepackage{tikz} % Variable definition to generate author note

% fix for \tightlist problem in pandoc 1.14
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Essential manuscript parts
  \title{A Validation of the Moral Foundations Questionnaire and Dictionary}

  \shorttitle{VALIDITY OF MFD}


  \author{Kayla N. Jordan\textsuperscript{1}, Erin M. Buchanan\textsuperscript{2}, \& William E. Padfield\textsuperscript{2}}

  \def\affdep{{"", "", ""}}%
  \def\affcity{{"", "", ""}}%

  \affiliation{
    \vspace{0.5cm}
          \textsuperscript{1} University of Texas - Austin\\
          \textsuperscript{2} Missouri State University  }

  \authornote{
    \newcounter{author}
    Kayla N. Jordan is a Ph.D.~candidate at the University of Texas at
    Austin. Erin M. Buchanan is an Associate Professor of Quantitative
    Psychology at Missouri State University. William E. Padfield is a
    masters degree candidate at Missouri State University.

                      Correspondence concerning this article should be addressed to Kayla N. Jordan, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}
                                    }


  \abstract{Enter abstract here. Each new line herein must be indented, like this
line.}
  \keywords{keywords \\

    
  }





\usepackage{amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{example}{Example}
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}

\maketitle

\setcounter{secnumdepth}{0}



Examining the construct and measurement validity of psychometric scales
can be difficult, especially for complex constructs such as morality.
Given the pervasiveness of language as avenue of moral justification and
moral argument, it is important to understand how language is indicative
of moral reasoning. Hence, the current study sought to examine the
validity of one approach to measuring moral language using the framework
of moral foundations theory, in comparison to traditional questionnaire
style measurements.

\section{Moral Foundations Theory}\label{moral-foundations-theory}

Moral Foundations Theory (MFT) was proposed by Haidt and Joseph (2004)
to explain the differences between political liberals' and
conservatives' moral thinking processes. The differences in party
processing were explained by variable focus on five moral foundations.
The first two of these foundations represents concerns for individuals.
The \emph{harm/care} foundation encompasses concerns of promoting
compassion and/or denigrating cruelty. The \emph{fairness/reciprocity}
foundation covers concerns of ensuring equality and justice. The next
three foundations represent concerns for the group. The
\emph{ingroup/loyalty} foundation encompasses concerns encouraging
patriotism and discouraging dissent. The \emph{authority/respect}
foundation represents concerns maintaining tradition and respecting
social hierarchies. The \emph{purity/sanctity} foundation encompasses
concerns engaging in virtues such as chastity and self-control and
abstaining from vices such as lust and gluttony. Throughout this
manuscript, we will use \emph{harm}, \emph{fairness}, \emph{ingroup},
\emph{authority}, and \emph{purity} to indicate the foundations and
their direction. For example, higher endorsement of the \emph{authority}
foundation implies a focus on basing moral judgments on respecting
tradition and hierarchy, while lower levels of endorsement imply basing
moral judgments less on respecting tradition and hierarchy and more on
other concerns. The endorsement along these moral foundation continuums
is related to political orientation. Namely, those of liberal political
orientation base moral judgments on the \emph{harm} and \emph{fairness}
foundations whereas those of conservative orientation based judgments on
all five foundations (Federico, Weber, Ergun, \& Hunt, 2013; Graham,
Haidt, \& Nosek, 2009; Graham, Nosek, \& Haidt, 2012; Weber \& Federico,
2013). Furthermore, Graham et al. (2012) found the differences between
the two sides of the political spectrum were exaggerated by the opposing
party. For example, liberals rated conservatives as more conservative
than conservatives rated themselves and vice versa. In addition to
political orientation, moral foundations also predicted specific policy
preferences and attitudes. Kertzer, Powers, Rathbun, and Iyer (2014)
found that higher endorsement of the \emph{ingroup}, \emph{authority},
and \emph{purity} foundations predicted support for the Iraq War and a
preemptive strike against Iran. However, higher endorsement of
\emph{harm} and \emph{fairness} foundations predicted support for the
Kyoto protocols. Koleva, Graham, Iyer, Ditto, and Haidt (2012) examined
the relationship between moral foundation endorsement and a wide range
of policy attitudes. Greater endorsement of the \emph{harm} foundation
predicted opposition to animal testing, the death penalty, and torture,
as well as support for gun control. Endorsement of the \emph{ingroup}
foundation predicted greater disapproval of flag burning and terrorism,
as well as greater support for defense spending. Finally, stronger
endorsement of \emph{purity} predicted opposition to abortion, same sex
marriage, teaching of evolution, and illegal immigration.

\section{Moral Foundations
Questionnaire}\label{moral-foundations-questionnaire}

The Moral Foundations Questionnaire (MFQ) was developed in order to
measure the extent to which an individual endorses each moral foundation
({\textbf{???}}). The MFQ is a 30-item scale divided into two subscales:
moral relevance and moral judgments. The 15 moral relevance items are
equally divided among the five foundations and examine how relevant a
condition is to making a moral judgment on a scale of 1 (\emph{not at
all relevant}) to 6 (\emph{extremely relevant}). These relevance items
include examples such as: \enquote{Whether or not someone used violence
(\emph{harm}),} \enquote{Whether or not someone was denied his or her
rights (\emph{fairness}),} \enquote{Whether or not someone showed a lack
of loyalty (\emph{ingroup}),} \enquote{Whether or not an action caused
chaos or disorder (\emph{authority}),} and \enquote{Whether or not
someone did something disgusting (\emph{purity}).} The moral judgments
items are also equally divided between the foundations and ask on a
six-point scale how much one agrees with each of the statements. These
judgment items include: \enquote{One of the worst things a person can do
is hurt a defenseless animal (\emph{harm}),} \enquote{Justice is the
most important requirement of a society (\emph{fairness}),} \enquote{I
am proud of my country's history (\emph{ingroup}),} \enquote{Men and
women each have different roles to play in society (\emph{authority}),}
and \enquote{Chastity is an important and valuable virtue
(\emph{purity}).} The internal consistency of this version from
({\textbf{???}}) was \(\alpha\) = .73 averaged across subscales with a
range of \(\alpha\) = .65-.84. Across six studies, the MFQ was found to
have an average Cronbach's alpha of .63 for \emph{harm}, .64 for
\emph{fairness}, .56 for \emph{ingroup}, .59 for \emph{authority}, and
.71 for \emph{purity} (Federico et al., 2013; Graham et al., 2009, 2012;
Weber \& Federico, 2013).Test-retest reliability was \emph{r} = .68-.82
using a sample of 123 college students. Confirmatory factor analysis
supported a well-fitted five-factor model (\emph{harm/care},
\emph{fairness/reciprocity}, \emph{ingroup/loyalty},
\emph{authority/respect}, and \emph{purity/sanctity}) over two,
individual (\emph{harm} and \emph{fairness}) versus group
(\emph{ingroup}, \emph{authority}, and \emph{purity}) foundations, or
three, autonomy (\emph{harm}, \emph{fairness}), community
(\emph{ingroup}, \emph{authority}), and divinity (\emph{purity}) ethics,
foundations factor model. The five-factor structure also fit for
non-Western samples, thus, providing evidence of the MFQ
generalizability. Convergent validity was supported with correlations on
other measures of morality (e.g.~Schwartz Value Scale (Schwartz, 1992 as
cited in ({\textbf{???}}))).

\section{Moral Foundations
Dictionary}\label{moral-foundations-dictionary}

Given the importance of language to political ideology and moral
thinking, Graham et al. (2009) developed a moral foundations dictionary
(MFD) to examine the use of moral justification in speech and/or
writing. A dictionary of roughly 50-60 words was developed for each
foundation. Words such as \emph{war} and \emph{peace} should indicate a
greater concern with \emph{harm} foundation whereas words such as
\emph{homeland} and \emph{terrorism} should indicate a greater concern
with the \emph{ingroup} foundation. The other foundation dictionaries
include \emph{equal} and \emph{justice} (\emph{fairness}), \emph{honor}
and \emph{protest} (\emph{authority}), and \emph{holy} and \emph{sin}
(\emph{purity}). To validate the word sets, Graham et al. (2009)
examined the frequency of MFD words in liberal and conservative sermons.
They found liberal ministers used \emph{harm}, \emph{fairness}, and
\emph{ingroup} words more often than conservative ministers who used
\emph{authority} and \emph{purity} words more often. Although
conservative ministers were expected to use more \emph{ingroup} words
based on political ideology and previous research, an examination of the
way liberal ministers used \emph{ingroup} words revealed a tendency for
the use of \emph{ingroup} words to glorify rebellion and promote
independence (i.e., the opposite direction from \emph{ingroup}
definitions). Effect sizes indicated relatively sizable difference
between liberal and conservative sermons with Cohen's \emph{d} ranging
from 0.56 to 1.27. Graham et al. (2009)'s validation focused on the
frequency of moral words as a dependent variable for the MFD. In
contrast to this approach, Sagi and Dehghani ({\textbf{???}}) explored
how moral words were used paired with other co-occurring concepts using
Latent Semantic Analysis (LSA). They examined three different moral
issues in different contexts to piece out specific moral words and their
collocates. First, they looked at how moral words were used in relation
to the World Trade Center compared to the Empire State Building in the
New York Times from 1987-2007. After 9-11, the number of moral words
associated with the World Trade Center increased, specifically
\emph{harm} words from the MFD. Second, they considered the changes in
how moral words were paired with mosque used in blogs as a response to
the debate of building a mosque near Ground Zero following 9-11. They
found words from the MFD were used more often with mosque during the
main debate and then the co-occurrence decreased afterwards. Lastly,
they examined moral language tied to the abortion debate in Congress.
Republicans used more moral language overall; more specifically,
Republicans tended to use more words associated with the \emph{purity}
foundation; while Democrats used more words associated with the
\emph{fairness} foundation.\\
These studies are the first steps at supporting the moral foundations
dictionary and questionnaire using the moral foundations framework. This
study combined both the dictionary and questionnaire to expand the
literature on their usefulness and psychometric properties due to the
dearth of studies on both measures. Therefore, the purpose of the
current study was to explore the reliability and validity of the MFD and
MFQ using the following procedures: 1) Cronbach's \(\alpha\) of both
measurement tools, as previous studies have shown mixed reliabilities 2)
a multi-method, multi-trait (MTMM) design comparing the MFD and MFQ on
one sample, and 3) the predictive validity of the MFD and MFQ to
political orientation.

\subsection{Method}\label{method}

\section{Sample 1}\label{sample-1}

Particpants. 290 participants were examined for this study as taken from
a larger investigation on priming political and religious attitudes
\emph{(PAPER REF)}. Participants were recruited via an online research
system (SONA) and were given course credit for their participation. The
sample consisted of 55.52\% men (\emph{n} = 161), 44.48\% women
(\emph{n} = 129), and was 80\% Caucasian with an average age of 20.02
(\emph{SD} = 3.07). Materials. Data was collected via an online survey
site (Qualtrics). Four fake new stories were presented to participants,
which were roughly 400 words each. First, all news stories included a
few sentences describing the use of chemical weapons in the Syrian civil
war. The news stories were manipulated with political (Republican v.
Democrat) and religious (religious v. not) quotes in a 2 x 2 design.
News stories can be provided upon request. Participants also completed
the 30-item version of the MFQ as described in the introduction. In
addition to basic demographics (gender, age, political orientation,
party affiliation, and religious affiliation), participant political
orientation was assessed with: \enquote{Rate your political orientation
on the following scale. 1 (\emph{conservative}) to 10 (\emph{liberal}).}
Procedure. After consenting to participate in the study, participants
were randomly shown one of the four new articles about Syria's use of
chemical weapons. Participants were then asked to write for 5-10 minutes
about their reaction to Syria's use of chemical weapons and the needed
response from the United States. After this section, participants then
completed the MFQ and demographics sections. \#Sample 2 Participants. A
total of 160 participants completed the second half of this study, which
was collected to increase sample size to examine the MFQ and MFD. The
sample included 29.63\% men (\emph{n} = 48) and 81.73\% women (\emph{n}
= 114) with 89\% identifying as Caucasian and an average age of 19.36
(\emph{SD} = 2.81). Participants were recruited and given course credit
in the same manner as sample 1. Materials. Data for this study was also
collected via Qualtrics with the same basic research design. The
following writing prompt was used, \enquote{Please write about your
attitudes on abortion (or same-sex marriage or environmentalism) as well
as your reason for this stance.} The three prompts were chosen to create
a more varied word set by using topics that should elicit words from
each moral foundations category by soliciting a moral response.
Participants again completed the MFQ, demographics, and the political
orientation scale from sample 1.\\
Procedure. After consenting to participate in this study, participants
were asked to write at least 1200 characters about their attitudes on
abortion, same-sex marriage, or environmentalism, which were randomly
assigned. Participants then completed the MFQ and demographics section.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{##find very small words}
\NormalTok{columndata =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata, }\DecValTok{2}\NormalTok{, sum) }
\NormalTok{correldata2 =}\StringTok{ }\NormalTok{correldata[ , columndata }\OperatorTok{>}\StringTok{ }\DecValTok{5}\NormalTok{]}

\NormalTok{allcorrels =}\StringTok{ }\KeywordTok{cor}\NormalTok{(correldata2[ , }\KeywordTok{c}\NormalTok{(}\DecValTok{2}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(correldata2))])}
\NormalTok{imptcorrels =}\StringTok{ }\KeywordTok{as.data.frame}\NormalTok{(allcorrels[}\OperatorTok{-}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\OperatorTok{:}\DecValTok{5}\NormalTok{,(}\KeywordTok{nrow}\NormalTok{(allcorrels)}\OperatorTok{-}\DecValTok{29}\NormalTok{)}\OperatorTok{:}\KeywordTok{nrow}\NormalTok{(allcorrels)) , }\DecValTok{1}\OperatorTok{:}\DecValTok{5}\NormalTok{])}

\NormalTok{M =}\StringTok{ }\KeywordTok{apply}\NormalTok{(imptcorrels, }\DecValTok{2}\NormalTok{, mean)}
\NormalTok{SD =}\StringTok{ }\KeywordTok{apply}\NormalTok{(imptcorrels, }\DecValTok{2}\NormalTok{, sd)}

\NormalTok{cutoffH =}\StringTok{ }\NormalTok{M }\OperatorTok{+}\StringTok{ }\DecValTok{2}\OperatorTok{*}\NormalTok{SD}
\NormalTok{cutoffL =}\StringTok{ }\NormalTok{M }\OperatorTok{-}\StringTok{ }\DecValTok{2}\OperatorTok{*}\NormalTok{SD}

\NormalTok{harmwords =}\StringTok{ }\KeywordTok{rownames}\NormalTok{(}\KeywordTok{subset}\NormalTok{(imptcorrels, harm }\OperatorTok{>}\StringTok{ }\NormalTok{cutoffH[}\StringTok{"harm"}\NormalTok{] }\OperatorTok{|}\StringTok{ }\NormalTok{harm }\OperatorTok{<}\StringTok{ }\NormalTok{cutoffL[}\StringTok{"harm"}\NormalTok{]))}
\NormalTok{fairwords =}\StringTok{ }\KeywordTok{rownames}\NormalTok{(}\KeywordTok{subset}\NormalTok{(imptcorrels, fair }\OperatorTok{>}\StringTok{ }\NormalTok{cutoffH[}\StringTok{"fair"}\NormalTok{] }\OperatorTok{|}\StringTok{ }\NormalTok{fair }\OperatorTok{<}\StringTok{ }\NormalTok{cutoffL[}\StringTok{"fair"}\NormalTok{]))}
\NormalTok{ingroupwords =}\StringTok{ }\KeywordTok{rownames}\NormalTok{(}\KeywordTok{subset}\NormalTok{(imptcorrels, ingroup }\OperatorTok{>}\StringTok{ }\NormalTok{cutoffH[}\StringTok{"ingroup"}\NormalTok{] }\OperatorTok{|}\StringTok{ }\NormalTok{ingroup }\OperatorTok{<}\StringTok{ }\NormalTok{cutoffL[}\StringTok{"ingroup"}\NormalTok{]))}
\NormalTok{authoritywords =}\StringTok{ }\KeywordTok{rownames}\NormalTok{(}\KeywordTok{subset}\NormalTok{(imptcorrels, authority }\OperatorTok{>}\StringTok{ }\NormalTok{cutoffH[}\StringTok{"authority"}\NormalTok{] }\OperatorTok{|}\StringTok{ }\NormalTok{authority }\OperatorTok{<}\StringTok{ }\NormalTok{cutoffL[}\StringTok{"authority"}\NormalTok{]))}
\NormalTok{puritywords =}\StringTok{ }\KeywordTok{rownames}\NormalTok{(}\KeywordTok{subset}\NormalTok{(imptcorrels, purity }\OperatorTok{>}\StringTok{ }\NormalTok{cutoffH[}\StringTok{"purity"}\NormalTok{] }\OperatorTok{|}\StringTok{ }\NormalTok{purity }\OperatorTok{<}\StringTok{ }\NormalTok{cutoffL[}\StringTok{"purity"}\NormalTok{]))}

\NormalTok{##the amount of times people used the words in THIS dataset on Syria}
\NormalTok{mtmmdata =}\StringTok{ }\NormalTok{correldata[ , }\DecValTok{1}\OperatorTok{:}\DecValTok{6}\NormalTok{]}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{h1 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , harmwords], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{f1 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , fairwords], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{i1 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , ingroupwords], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{a1 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , authoritywords], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{p1 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , puritywords], }\DecValTok{1}\NormalTok{, sum)}

\NormalTok{##the amount of time people used the original MFD words}
\NormalTok{original_mfd =}\StringTok{ }\KeywordTok{read.csv}\NormalTok{(}\StringTok{"original_mfd.csv"}\NormalTok{, }\DataTypeTok{stringsAsFactors =}\NormalTok{ F)}

\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{h2 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , original_mfd}\OperatorTok{$}\NormalTok{h2[}\DecValTok{1}\OperatorTok{:}\DecValTok{26}\NormalTok{] ], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{f2 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , original_mfd}\OperatorTok{$}\NormalTok{f2[}\DecValTok{1}\OperatorTok{:}\DecValTok{19}\NormalTok{] ], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{i2 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , original_mfd}\OperatorTok{$}\NormalTok{i2[}\DecValTok{1}\OperatorTok{:}\DecValTok{15}\NormalTok{] ], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{a2 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , original_mfd}\OperatorTok{$}\NormalTok{a2[}\DecValTok{1}\OperatorTok{:}\DecValTok{30}\NormalTok{] ], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{p2 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , original_mfd}\OperatorTok{$}\NormalTok{p2[}\DecValTok{1}\OperatorTok{:}\DecValTok{20}\NormalTok{] ], }\DecValTok{1}\NormalTok{, sum)}

\NormalTok{##the amount of times people used the new dictionary words from the norming study}
\NormalTok{new_data =}\StringTok{ }\KeywordTok{read.csv}\NormalTok{(}\StringTok{"new_data.csv"}\NormalTok{, }\DataTypeTok{stringsAsFactors =}\NormalTok{ F)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{h3 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , new_data}\OperatorTok{$}\NormalTok{h3[}\DecValTok{1}\OperatorTok{:}\DecValTok{24}\NormalTok{] ], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{f3 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , new_data}\OperatorTok{$}\NormalTok{f3[}\DecValTok{1}\OperatorTok{:}\DecValTok{21}\NormalTok{] ], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{i3 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , new_data}\OperatorTok{$}\NormalTok{i3[}\DecValTok{1}\OperatorTok{:}\DecValTok{11}\NormalTok{] ], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{a3 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , new_data}\OperatorTok{$}\NormalTok{a3[}\DecValTok{1}\OperatorTok{:}\DecValTok{16}\NormalTok{] ], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{p3 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , new_data}\OperatorTok{$}\NormalTok{p3[}\DecValTok{1}\OperatorTok{:}\DecValTok{21}\NormalTok{] ], }\DecValTok{1}\NormalTok{, sum)}

\NormalTok{##remember that original data is number 2}

\NormalTok{##intersection data original + 1}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{h12 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , }\KeywordTok{unique}\NormalTok{(}\KeywordTok{c}\NormalTok{(original_mfd}\OperatorTok{$}\NormalTok{h2[}\DecValTok{1}\OperatorTok{:}\DecValTok{26}\NormalTok{], harmwords))], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{f12 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , }\KeywordTok{unique}\NormalTok{(}\KeywordTok{c}\NormalTok{(original_mfd}\OperatorTok{$}\NormalTok{f2[}\DecValTok{1}\OperatorTok{:}\DecValTok{19}\NormalTok{], fairwords)) ], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{i12 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , }\KeywordTok{unique}\NormalTok{(}\KeywordTok{c}\NormalTok{(original_mfd}\OperatorTok{$}\NormalTok{i2[}\DecValTok{1}\OperatorTok{:}\DecValTok{15}\NormalTok{], ingroupwords)) ], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{a12 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , }\KeywordTok{unique}\NormalTok{(}\KeywordTok{c}\NormalTok{(original_mfd}\OperatorTok{$}\NormalTok{a2[}\DecValTok{1}\OperatorTok{:}\DecValTok{30}\NormalTok{], authoritywords)) ], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{p12 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , }\KeywordTok{unique}\NormalTok{(}\KeywordTok{c}\NormalTok{(original_mfd}\OperatorTok{$}\NormalTok{p2[}\DecValTok{1}\OperatorTok{:}\DecValTok{20}\NormalTok{], puritywords)) ], }\DecValTok{1}\NormalTok{, sum)}

\NormalTok{##intersection data original + 3}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{h23 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , }\KeywordTok{unique}\NormalTok{(}\KeywordTok{c}\NormalTok{(original_mfd}\OperatorTok{$}\NormalTok{h2[}\DecValTok{1}\OperatorTok{:}\DecValTok{26}\NormalTok{], new_data}\OperatorTok{$}\NormalTok{h3[}\DecValTok{1}\OperatorTok{:}\DecValTok{24}\NormalTok{]))], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{f23 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , }\KeywordTok{unique}\NormalTok{(}\KeywordTok{c}\NormalTok{(original_mfd}\OperatorTok{$}\NormalTok{f2[}\DecValTok{1}\OperatorTok{:}\DecValTok{19}\NormalTok{], new_data}\OperatorTok{$}\NormalTok{f3[}\DecValTok{1}\OperatorTok{:}\DecValTok{21}\NormalTok{])) ], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{i23 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , }\KeywordTok{unique}\NormalTok{(}\KeywordTok{c}\NormalTok{(original_mfd}\OperatorTok{$}\NormalTok{i2[}\DecValTok{1}\OperatorTok{:}\DecValTok{15}\NormalTok{], new_data}\OperatorTok{$}\NormalTok{i3[}\DecValTok{1}\OperatorTok{:}\DecValTok{11}\NormalTok{])) ], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{a23 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , }\KeywordTok{unique}\NormalTok{(}\KeywordTok{c}\NormalTok{(original_mfd}\OperatorTok{$}\NormalTok{a2[}\DecValTok{1}\OperatorTok{:}\DecValTok{30}\NormalTok{], new_data}\OperatorTok{$}\NormalTok{a3[}\DecValTok{1}\OperatorTok{:}\DecValTok{16}\NormalTok{] )) ], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{p23 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , }\KeywordTok{unique}\NormalTok{(}\KeywordTok{c}\NormalTok{(original_mfd}\OperatorTok{$}\NormalTok{p2[}\DecValTok{1}\OperatorTok{:}\DecValTok{20}\NormalTok{], new_data}\OperatorTok{$}\NormalTok{p3[}\DecValTok{1}\OperatorTok{:}\DecValTok{21}\NormalTok{] )) ], }\DecValTok{1}\NormalTok{, sum)}

\NormalTok{##intersection data all}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{h123 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , }\KeywordTok{unique}\NormalTok{(}\KeywordTok{c}\NormalTok{(original_mfd}\OperatorTok{$}\NormalTok{h2[}\DecValTok{1}\OperatorTok{:}\DecValTok{26}\NormalTok{], harmwords, new_data}\OperatorTok{$}\NormalTok{h3[}\DecValTok{1}\OperatorTok{:}\DecValTok{24}\NormalTok{]))], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{f123 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , }\KeywordTok{unique}\NormalTok{(}\KeywordTok{c}\NormalTok{(original_mfd}\OperatorTok{$}\NormalTok{f2[}\DecValTok{1}\OperatorTok{:}\DecValTok{19}\NormalTok{], fairwords, new_data}\OperatorTok{$}\NormalTok{f3[}\DecValTok{1}\OperatorTok{:}\DecValTok{21}\NormalTok{])) ], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{i123 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , }\KeywordTok{unique}\NormalTok{(}\KeywordTok{c}\NormalTok{(original_mfd}\OperatorTok{$}\NormalTok{i2[}\DecValTok{1}\OperatorTok{:}\DecValTok{15}\NormalTok{], ingroupwords, new_data}\OperatorTok{$}\NormalTok{i3[}\DecValTok{1}\OperatorTok{:}\DecValTok{11}\NormalTok{])) ], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{a123 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , }\KeywordTok{unique}\NormalTok{(}\KeywordTok{c}\NormalTok{(original_mfd}\OperatorTok{$}\NormalTok{a2[}\DecValTok{1}\OperatorTok{:}\DecValTok{30}\NormalTok{], authoritywords, new_data}\OperatorTok{$}\NormalTok{a3[}\DecValTok{1}\OperatorTok{:}\DecValTok{16}\NormalTok{] )) ], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata}\OperatorTok{$}\NormalTok{p123 =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , }\KeywordTok{unique}\NormalTok{(}\KeywordTok{c}\NormalTok{(original_mfd}\OperatorTok{$}\NormalTok{p2[}\DecValTok{1}\OperatorTok{:}\DecValTok{20}\NormalTok{], puritywords, new_data}\OperatorTok{$}\NormalTok{p3[}\DecValTok{1}\OperatorTok{:}\DecValTok{21}\NormalTok{] )) ], }\DecValTok{1}\NormalTok{, sum)}

\NormalTok{##normalize the whole damn thing}
\NormalTok{totalwords =}\StringTok{ }\KeywordTok{apply}\NormalTok{(correldata[ , }\DecValTok{7}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(correldata)], }\DecValTok{1}\NormalTok{, sum)}
\NormalTok{mtmmdata[ , }\DecValTok{7}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(mtmmdata)] =}\StringTok{ }\NormalTok{mtmmdata[ , }\DecValTok{7}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(mtmmdata)]}\OperatorTok{/}\NormalTok{totalwords}\OperatorTok{*}\DecValTok{100}
\NormalTok{mtmmdata =}\StringTok{ }\KeywordTok{cbind}\NormalTok{(mtmmdata, correldata[ , }\DecValTok{2049}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(correldata)])}

\NormalTok{##now run some MTMM!}
\KeywordTok{library}\NormalTok{(semPlot)}
\KeywordTok{library}\NormalTok{(lavaan)}

\NormalTok{####mtmm our data correlation 1####}
\NormalTok{model1 =}\StringTok{ '}
\StringTok{harmL =~ X1+X2+X3+X4+X5+X6+h1}
\StringTok{fairL =~ X7+X8+X9+X10+X11+X12+f1}
\StringTok{ingroupL =~ X13+X14+X15+X16+X17+X18+i1}
\StringTok{authorityL =~ X19+X20+X21+X22+X23+X24+a1}
\StringTok{purityL=~ X25+X26+X27+X28+X29+X30+p1}
\StringTok{mfq =~ X1+X2+X3+X4+X5+X6+X7+X8+X9+X10+X11+X12+X13+X14+X15+X16+X17+X18+X19+X20+X21+X22+X23+X24+X25+X26+X27+X28+X29+X30}
\StringTok{mfd =~ h1+f1+i1+a1+p1}

\StringTok{##fix the covariances}
\StringTok{harmL~~0*mfq}
\StringTok{fairL~~0*mfq}
\StringTok{ingroupL~~0*mfq}
\StringTok{authorityL~~0*mfq}
\StringTok{purityL~~0*mfq}
\StringTok{harmL~~0*mfd}
\StringTok{fairL~~0*mfd}
\StringTok{ingroupL~~0*mfd}
\StringTok{authorityL~~0*mfd}
\StringTok{purityL~~0*mfd}
\StringTok{ingroupL~~-.29*harmL}
\StringTok{f1~~1.35*f1}
\StringTok{'}

\NormalTok{model1.fit =}\StringTok{ }\KeywordTok{cfa}\NormalTok{(model1, }\DataTypeTok{data=}\NormalTok{mtmmdata, }\DataTypeTok{std.lv=}\OtherTok{TRUE}\NormalTok{)}
\KeywordTok{summary}\NormalTok{(model1.fit, }\DataTypeTok{rsquare=}\OtherTok{TRUE}\NormalTok{, }\DataTypeTok{standardized=}\OtherTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## lavaan (0.5-23.1097) converged normally after  57 iterations
## 
##   Number of observations                           160
## 
##   Estimator                                         ML
##   Minimum Function Test Statistic              854.603
##   Degrees of freedom                               516
##   P-value (Chi-square)                           0.000
## 
## Parameter Estimates:
## 
##   Information                                 Expected
##   Standard Errors                             Standard
## 
## Latent Variables:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   harmL =~                                                              
##     X1               -0.214    0.086   -2.490    0.013   -0.214   -0.206
##     X2               -0.057    0.095   -0.595    0.552   -0.057   -0.049
##     X3               -0.298    0.093   -3.210    0.001   -0.298   -0.281
##     X4                0.615    0.104    5.918    0.000    0.615    0.574
##     X5                0.357    0.088    4.059    0.000    0.357    0.333
##     X6                0.134    0.088    1.521    0.128    0.134    0.126
##     h1                0.103    0.067    1.541    0.123    0.103    0.116
##   fairL =~                                                              
##     X7                0.807    0.100    8.061    0.000    0.807    0.602
##     X8                0.861    0.082   10.470    0.000    0.861    0.685
##     X9                0.932    0.081   11.447    0.000    0.932    0.753
##     X10               1.002    0.084   11.948    0.000    1.002    0.801
##     X11               0.968    0.110    8.798    0.000    0.968    0.652
##     X12               0.576    0.086    6.720    0.000    0.576    0.492
##     f1               -0.244    0.103   -2.366    0.018   -0.244   -0.174
##   ingroupL =~                                                           
##     X13               1.085    0.099   10.911    0.000    1.085    0.766
##     X14               0.901    0.110    8.165    0.000    0.901    0.612
##     X15               1.438    0.130   11.067    0.000    1.438    0.782
##     X16               0.184    0.073    2.535    0.011    0.184    0.187
##     X17              -0.204    0.121   -1.689    0.091   -0.204   -0.142
##     X18               0.440    0.128    3.429    0.001    0.440    0.284
##     i1                0.058    0.065    0.888    0.375    0.058    0.075
##   authorityL =~                                                         
##     X19               0.213    0.105    2.024    0.043    0.213    0.168
##     X20               0.245    0.102    2.389    0.017    0.245    0.203
##     X21               0.035    0.133    0.260    0.795    0.035    0.023
##     X22               0.747    0.108    6.904    0.000    0.747    0.557
##     X23               1.032    0.111    9.308    0.000    1.032    0.725
##     X24               0.832    0.110    7.539    0.000    0.832    0.599
##     a1               -0.334    0.109   -3.078    0.002   -0.334   -0.268
##   purityL =~                                                            
##     X25               0.644    0.093    6.938    0.000    0.644    0.539
##     X26               0.814    0.114    7.169    0.000    0.814    0.542
##     X27               0.535    0.102    5.266    0.000    0.535    0.418
##     X28               0.679    0.115    5.912    0.000    0.679    0.470
##     X29               0.923    0.103    8.947    0.000    0.923    0.657
##     X30               1.234    0.118   10.481    0.000    1.234    0.748
##     p1               -0.493    0.096   -5.120    0.000   -0.493   -0.410
##   mfq =~                                                                
##     X1                0.799    0.073   10.915    0.000    0.799    0.768
##     X2                0.818    0.081   10.166    0.000    0.818    0.713
##     X3                0.928    0.071   13.014    0.000    0.928    0.876
##     X4                0.843    0.085    9.888    0.000    0.843    0.787
##     X5                0.809    0.079   10.236    0.000    0.809    0.754
##     X6                0.732    0.076    9.675    0.000    0.732    0.690
##     X7                0.210    0.107    1.956    0.050    0.210    0.156
##     X8                0.511    0.096    5.305    0.000    0.511    0.407
##     X9                0.401    0.096    4.161    0.000    0.401    0.324
##     X10               0.240    0.099    2.432    0.015    0.240    0.192
##     X11              -0.095    0.119   -0.795    0.426   -0.095   -0.064
##     X12               0.419    0.091    4.590    0.000    0.419    0.358
##     X13               0.225    0.113    1.985    0.047    0.225    0.159
##     X14               0.265    0.118    2.252    0.024    0.265    0.180
##     X15              -0.113    0.147   -0.766    0.444   -0.113   -0.061
##     X16               0.529    0.074    7.139    0.000    0.529    0.536
##     X17               0.226    0.116    1.946    0.052    0.226    0.157
##     X18               0.177    0.125    1.417    0.156    0.177    0.115
##     X19               0.462    0.099    4.650    0.000    0.462    0.365
##     X20               0.338    0.096    3.523    0.000    0.338    0.280
##     X21               0.076    0.122    0.618    0.537    0.076    0.050
##     X22              -0.205    0.106   -1.924    0.054   -0.205   -0.153
##     X23              -0.105    0.112   -0.930    0.352   -0.105   -0.073
##     X24              -0.243    0.110   -2.214    0.027   -0.243   -0.175
##     X25               0.059    0.095    0.614    0.539    0.059    0.049
##     X26              -0.350    0.118   -2.963    0.003   -0.350   -0.233
##     X27              -0.233    0.102   -2.285    0.022   -0.233   -0.182
##     X28               0.027    0.116    0.233    0.816    0.027    0.019
##     X29              -0.212    0.110   -1.919    0.055   -0.212   -0.151
##     X30              -0.043    0.130   -0.331    0.741   -0.043   -0.026
##   mfd =~                                                                
##     h1                0.799    0.109    7.324    0.000    0.799    0.899
##     f1                0.750    0.131    5.746    0.000    0.750    0.534
##     i1                0.045    0.066    0.682    0.495    0.045    0.059
##     a1               -0.065    0.105   -0.622    0.534   -0.065   -0.052
##     p1                0.184    0.098    1.878    0.060    0.184    0.153
## 
## Covariances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   harmL ~~                                                              
##     mfq               0.000                               0.000    0.000
##   fairL ~~                                                              
##     mfq               0.000                               0.000    0.000
##   ingroupL ~~                                                           
##     mfq               0.000                               0.000    0.000
##   authorityL ~~                                                         
##     mfq               0.000                               0.000    0.000
##   purityL ~~                                                            
##     mfq               0.000                               0.000    0.000
##   harmL ~~                                                              
##     mfd               0.000                               0.000    0.000
##   fairL ~~                                                              
##     mfd               0.000                               0.000    0.000
##   ingroupL ~~                                                           
##     mfd               0.000                               0.000    0.000
##   authorityL ~~                                                         
##     mfd               0.000                               0.000    0.000
##   purityL ~~                                                            
##     mfd               0.000                               0.000    0.000
##   harmL ~~                                                              
##     ingroupL         -0.290                              -0.290   -0.290
##     fairL            -0.150    0.077   -1.942    0.052   -0.150   -0.150
##     authorityL       -0.259    0.093   -2.793    0.005   -0.259   -0.259
##     purityL          -0.274    0.073   -3.768    0.000   -0.274   -0.274
##   fairL ~~                                                              
##     ingroupL          0.717    0.057   12.671    0.000    0.717    0.717
##     authorityL        0.531    0.081    6.554    0.000    0.531    0.531
##     purityL           0.587    0.070    8.393    0.000    0.587    0.587
##   ingroupL ~~                                                           
##     authorityL        0.535    0.085    6.307    0.000    0.535    0.535
##     purityL           0.836    0.050   16.874    0.000    0.836    0.836
##   authorityL ~~                                                         
##     purityL           0.850    0.058   14.727    0.000    0.850    0.850
##   mfq ~~                                                                
##     mfd              -0.291    0.089   -3.281    0.001   -0.291   -0.291
## 
## Variances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##    .f1                1.350                               1.350    0.684
##    .X1                0.397    0.057    6.959    0.000    0.397    0.368
##    .X2                0.646    0.079    8.226    0.000    0.646    0.490
##    .X3                0.173    0.054    3.234    0.001    0.173    0.154
##    .X4                0.059    0.088    0.669    0.503    0.059    0.052
##    .X5                0.370    0.058    6.351    0.000    0.370    0.321
##    .X6                0.570    0.067    8.472    0.000    0.570    0.508
##    .h1                0.140    0.152    0.918    0.358    0.140    0.178
##    .X7                1.100    0.134    8.239    0.000    1.100    0.613
##    .X8                0.577    0.079    7.348    0.000    0.577    0.365
##    .X9                0.504    0.074    6.852    0.000    0.504    0.329
##    .X10               0.504    0.077    6.527    0.000    0.504    0.322
##    .X11               1.257    0.158    7.981    0.000    1.257    0.571
##    .X12               0.861    0.102    8.455    0.000    0.861    0.629
##    .X13               0.779    0.118    6.584    0.000    0.779    0.388
##    .X14               1.282    0.161    7.982    0.000    1.282    0.592
##    .X15               1.305    0.202    6.451    0.000    1.305    0.385
##    .X16               0.659    0.076    8.651    0.000    0.659    0.678
##    .X17               1.982    0.223    8.898    0.000    1.982    0.955
##    .X18               2.166    0.246    8.809    0.000    2.166    0.906
##    .i1                0.579    0.065    8.929    0.000    0.579    0.991
##    .X19               1.345    0.153    8.771    0.000    1.345    0.839
##    .X20               1.283    0.146    8.779    0.000    1.283    0.880
##    .X21               2.254    0.252    8.942    0.000    2.254    0.997
##    .X22               1.195    0.153    7.822    0.000    1.195    0.666
##    .X23               0.951    0.156    6.109    0.000    0.951    0.469
##    .X24               1.180    0.157    7.517    0.000    1.180    0.611
##    .a1                1.440    0.164    8.757    0.000    1.440    0.926
##    .X25               1.008    0.120    8.383    0.000    1.008    0.707
##    .X26               1.468    0.177    8.304    0.000    1.468    0.652
##    .X27               1.299    0.150    8.635    0.000    1.299    0.792
##    .X28               1.624    0.190    8.563    0.000    1.624    0.779
##    .X29               1.075    0.137    7.839    0.000    1.075    0.545
##    .X30               1.199    0.168    7.125    0.000    1.199    0.440
##    .p1                1.172    0.136    8.609    0.000    1.172    0.809
##     harmL             1.000                               1.000    1.000
##     fairL             1.000                               1.000    1.000
##     ingroupL          1.000                               1.000    1.000
##     authorityL        1.000                               1.000    1.000
##     purityL           1.000                               1.000    1.000
##     mfq               1.000                               1.000    1.000
##     mfd               1.000                               1.000    1.000
## 
## R-Square:
##                    Estimate
##     f1                0.316
##     X1                0.632
##     X2                0.510
##     X3                0.846
##     X4                0.948
##     X5                0.679
##     X6                0.492
##     h1                0.822
##     X7                0.387
##     X8                0.635
##     X9                0.671
##     X10               0.678
##     X11               0.429
##     X12               0.371
##     X13               0.612
##     X14               0.408
##     X15               0.615
##     X16               0.322
##     X17               0.045
##     X18               0.094
##     i1                0.009
##     X19               0.161
##     X20               0.120
##     X21               0.003
##     X22               0.334
##     X23               0.531
##     X24               0.389
##     a1                0.074
##     X25               0.293
##     X26               0.348
##     X27               0.208
##     X28               0.221
##     X29               0.455
##     X30               0.560
##     p1                0.191
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#semPaths(model1.fit, whatLabels = "std", layout = "tree")}
\KeywordTok{fitMeasures}\NormalTok{(model1.fit, }\DataTypeTok{fit.measures =} \StringTok{"aic"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##      aic 
## 16876.57
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{####mtmm original data 2####}
\NormalTok{model2 =}\StringTok{ '}
\StringTok{harmL =~ X1+X2+X3+X4+X5+X6+h2}
\StringTok{fairL =~ X7+X8+X9+X10+X11+X12+f2}
\StringTok{ingroupL =~ X13+X14+X15+X16+X17+X18+i2}
\StringTok{authorityL =~ X19+X20+X21+X22+X23+X24+a2}
\StringTok{purityL=~ X25+X26+X27+X28+X29+X30+p2}
\StringTok{mfq =~ X1+X2+X3+X4+X5+X6+X7+X8+X9+X10+X11+X12+X13+X14+X15+X16+X17+X18+X19+X20+X21+X22+X23+X24+X25+X26+X27+X28+X29+X30}
\StringTok{mfd =~ h2+f2+i2+a2+p2}

\StringTok{##fix the covariances}
\StringTok{harmL~~0*mfq}
\StringTok{fairL~~0*mfq}
\StringTok{ingroupL~~0*mfq}
\StringTok{authorityL~~0*mfq}
\StringTok{purityL~~0*mfq}
\StringTok{harmL~~0*mfd}
\StringTok{fairL~~0*mfd}
\StringTok{ingroupL~~0*mfd}
\StringTok{authorityL~~0*mfd}
\StringTok{purityL~~0*mfd}
\StringTok{a2~~1.56*a2}
\StringTok{h2~~2.14*h2}
\StringTok{f2~~1.84*f2}
\StringTok{'}

\NormalTok{model2.fit =}\StringTok{ }\KeywordTok{cfa}\NormalTok{(model2, }\DataTypeTok{data=}\NormalTok{mtmmdata, }\DataTypeTok{std.lv=}\OtherTok{TRUE}\NormalTok{)}
\KeywordTok{summary}\NormalTok{(model2.fit, }\DataTypeTok{rsquare=}\OtherTok{TRUE}\NormalTok{, }\DataTypeTok{standardized=}\OtherTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## lavaan (0.5-23.1097) converged normally after  65 iterations
## 
##   Number of observations                           160
## 
##   Estimator                                         ML
##   Minimum Function Test Statistic             1203.980
##   Degrees of freedom                               517
##   P-value (Chi-square)                           0.000
## 
## Parameter Estimates:
## 
##   Information                                 Expected
##   Standard Errors                             Standard
## 
## Latent Variables:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   harmL =~                                                              
##     X1               -0.125    0.083   -1.517    0.129   -0.125   -0.120
##     X2                0.031    0.092    0.338    0.736    0.031    0.027
##     X3               -0.197    0.087   -2.257    0.024   -0.197   -0.183
##     X4                0.692    0.095    7.265    0.000    0.692    0.671
##     X5                0.442    0.085    5.209    0.000    0.442    0.421
##     X6                0.204    0.084    2.420    0.016    0.204    0.195
##     h2                0.343    0.173    1.987    0.047    0.343    0.150
##   fairL =~                                                              
##     X7                0.822    0.100    8.232    0.000    0.822    0.603
##     X8                0.871    0.082   10.568    0.000    0.871    0.664
##     X9                0.945    0.081   11.603    0.000    0.945    0.733
##     X10               1.005    0.084   11.974    0.000    1.005    0.779
##     X11               1.007    0.109    9.265    0.000    1.007    0.677
##     X12               0.586    0.085    6.899    0.000    0.586    0.487
##     f2                1.357    0.146    9.283    0.000    1.357    0.620
##   ingroupL =~                                                           
##     X13               1.083    0.100   10.842    0.000    1.083    0.753
##     X14               0.917    0.110    8.308    0.000    0.917    0.616
##     X15               1.423    0.131   10.875    0.000    1.423    0.776
##     X16               0.174    0.072    2.428    0.015    0.174    0.175
##     X17              -0.222    0.121   -1.839    0.066   -0.222   -0.155
##     X18               0.421    0.129    3.273    0.001    0.421    0.271
##     i2                0.045    0.028    1.574    0.116    0.045    0.134
##   authorityL =~                                                         
##     X19               0.276    0.103    2.684    0.007    0.276    0.214
##     X20               0.296    0.100    2.955    0.003    0.296    0.241
##     X21               0.124    0.132    0.944    0.345    0.124    0.083
##     X22               0.772    0.107    7.241    0.000    0.772    0.579
##     X23               1.044    0.109    9.616    0.000    1.044    0.726
##     X24               0.895    0.108    8.307    0.000    0.895    0.648
##     a2                0.961    0.131    7.343    0.000    0.961    0.530
##   purityL =~                                                            
##     X25               0.653    0.093    7.022    0.000    0.653    0.540
##     X26               0.819    0.114    7.194    0.000    0.819    0.553
##     X27               0.536    0.102    5.256    0.000    0.536    0.422
##     X28               0.688    0.115    5.979    0.000    0.688    0.474
##     X29               0.925    0.104    8.913    0.000    0.925    0.663
##     X30               1.230    0.119   10.323    0.000    1.230    0.739
##     p2                0.024    0.045    0.545    0.586    0.024    0.046
##   mfq =~                                                                
##     X1                0.824    0.072   11.489    0.000    0.824    0.787
##     X2                0.816    0.081   10.109    0.000    0.816    0.712
##     X3                0.966    0.069   13.955    0.000    0.966    0.900
##     X4                0.722    0.086    8.432    0.000    0.722    0.700
##     X5                0.733    0.080    9.187    0.000    0.733    0.699
##     X6                0.703    0.076    9.204    0.000    0.703    0.670
##     X7                0.308    0.104    2.955    0.003    0.308    0.226
##     X8                0.622    0.094    6.648    0.000    0.622    0.474
##     X9                0.519    0.092    5.635    0.000    0.519    0.403
##     X10               0.381    0.093    4.076    0.000    0.381    0.295
##     X11               0.038    0.114    0.333    0.739    0.038    0.025
##     X12               0.512    0.090    5.678    0.000    0.512    0.426
##     X13               0.347    0.111    3.136    0.002    0.347    0.241
##     X14               0.345    0.117    2.962    0.003    0.345    0.232
##     X15               0.054    0.143    0.376    0.707    0.054    0.029
##     X16               0.554    0.075    7.419    0.000    0.554    0.556
##     X17               0.221    0.117    1.894    0.058    0.221    0.154
##     X18               0.230    0.126    1.828    0.068    0.230    0.148
##     X19               0.535    0.100    5.334    0.000    0.535    0.415
##     X20               0.423    0.097    4.371    0.000    0.423    0.345
##     X21               0.093    0.123    0.759    0.448    0.093    0.062
##     X22              -0.034    0.105   -0.326    0.745   -0.034   -0.026
##     X23               0.135    0.111    1.215    0.224    0.135    0.094
##     X24              -0.047    0.108   -0.431    0.666   -0.047   -0.034
##     X25               0.193    0.096    2.008    0.045    0.193    0.159
##     X26              -0.207    0.117   -1.761    0.078   -0.207   -0.140
##     X27              -0.131    0.102   -1.286    0.198   -0.131   -0.103
##     X28               0.135    0.117    1.156    0.248    0.135    0.093
##     X29              -0.053    0.110   -0.486    0.627   -0.053   -0.038
##     X30               0.171    0.130    1.320    0.187    0.171    0.103
##   mfd =~                                                                
##     h2                1.724    0.165   10.463    0.000    1.724    0.754
##     f2                1.055    0.157    6.733    0.000    1.055    0.482
##     i2               -0.026    0.031   -0.856    0.392   -0.026   -0.079
##     a2                0.900    0.139    6.488    0.000    0.900    0.496
##     p2                0.042    0.049    0.855    0.392    0.042    0.079
## 
## Covariances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   harmL ~~                                                              
##     mfq               0.000                               0.000    0.000
##   fairL ~~                                                              
##     mfq               0.000                               0.000    0.000
##   ingroupL ~~                                                           
##     mfq               0.000                               0.000    0.000
##   authorityL ~~                                                         
##     mfq               0.000                               0.000    0.000
##   purityL ~~                                                            
##     mfq               0.000                               0.000    0.000
##   harmL ~~                                                              
##     mfd               0.000                               0.000    0.000
##   fairL ~~                                                              
##     mfd               0.000                               0.000    0.000
##   ingroupL ~~                                                           
##     mfd               0.000                               0.000    0.000
##   authorityL ~~                                                         
##     mfd               0.000                               0.000    0.000
##   purityL ~~                                                            
##     mfd               0.000                               0.000    0.000
##   harmL ~~                                                              
##     fairL            -0.055    0.097   -0.563    0.574   -0.055   -0.055
##     ingroupL         -0.167    0.097   -1.726    0.084   -0.167   -0.167
##     authorityL       -0.234    0.098   -2.396    0.017   -0.234   -0.234
##     purityL          -0.239    0.095   -2.520    0.012   -0.239   -0.239
##   fairL ~~                                                              
##     ingroupL          0.717    0.056   12.881    0.000    0.717    0.717
##     authorityL        0.492    0.079    6.213    0.000    0.492    0.492
##     purityL           0.561    0.072    7.750    0.000    0.561    0.561
##   ingroupL ~~                                                           
##     authorityL        0.494    0.084    5.849    0.000    0.494    0.494
##     purityL           0.829    0.051   16.112    0.000    0.829    0.829
##   authorityL ~~                                                         
##     purityL           0.830    0.055   15.125    0.000    0.830    0.830
##   mfq ~~                                                                
##     mfd               0.558    0.076    7.361    0.000    0.558    0.558
## 
## Variances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##    .a2                1.560                               1.560    0.474
##    .h2                2.140                               2.140    0.409
##    .f2                1.840                               1.840    0.384
##    .X1                0.401    0.057    7.074    0.000    0.401    0.366
##    .X2                0.648    0.079    8.246    0.000    0.648    0.493
##    .X3                0.179    0.052    3.462    0.001    0.179    0.156
##    .X4                0.063    0.093    0.679    0.497    0.063    0.059
##    .X5                0.367    0.060    6.134    0.000    0.367    0.334
##    .X6                0.565    0.067    8.456    0.000    0.565    0.513
##    .X7                1.089    0.131    8.293    0.000    1.089    0.586
##    .X8                0.577    0.077    7.497    0.000    0.577    0.335
##    .X9                0.499    0.071    7.038    0.000    0.499    0.300
##    .X10               0.510    0.075    6.843    0.000    0.510    0.306
##    .X11               1.194    0.150    7.955    0.000    1.194    0.540
##    .X12               0.842    0.099    8.470    0.000    0.842    0.581
##    .X13               0.775    0.118    6.571    0.000    0.775    0.375
##    .X14               1.257    0.159    7.926    0.000    1.257    0.567
##    .X15               1.338    0.205    6.534    0.000    1.338    0.398
##    .X16               0.656    0.076    8.606    0.000    0.656    0.661
##    .X17               1.965    0.221    8.883    0.000    1.965    0.952
##    .X18               2.178    0.247    8.819    0.000    2.178    0.904
##    .i2                0.109    0.012    8.894    0.000    0.109    0.976
##    .X19               1.299    0.149    8.696    0.000    1.299    0.782
##    .X20               1.240    0.142    8.719    0.000    1.240    0.823
##    .X21               2.242    0.251    8.928    0.000    2.242    0.989
##    .X22               1.182    0.150    7.878    0.000    1.182    0.664
##    .X23               0.963    0.148    6.517    0.000    0.963    0.465
##    .X24               1.105    0.149    7.394    0.000    1.105    0.579
##    .X25               0.998    0.119    8.354    0.000    0.998    0.683
##    .X26               1.477    0.178    8.288    0.000    1.477    0.674
##    .X27               1.309    0.152    8.633    0.000    1.309    0.811
##    .X28               1.618    0.189    8.550    0.000    1.618    0.767
##    .X29               1.086    0.139    7.829    0.000    1.086    0.559
##    .X30               1.228    0.172    7.145    0.000    1.228    0.443
##    .p2                0.276    0.031    8.922    0.000    0.276    0.992
##     harmL             1.000                               1.000    1.000
##     fairL             1.000                               1.000    1.000
##     ingroupL          1.000                               1.000    1.000
##     authorityL        1.000                               1.000    1.000
##     purityL           1.000                               1.000    1.000
##     mfq               1.000                               1.000    1.000
##     mfd               1.000                               1.000    1.000
## 
## R-Square:
##                    Estimate
##     a2                0.526
##     h2                0.591
##     f2                0.616
##     X1                0.634
##     X2                0.507
##     X3                0.844
##     X4                0.941
##     X5                0.666
##     X6                0.487
##     X7                0.414
##     X8                0.665
##     X9                0.700
##     X10               0.694
##     X11               0.460
##     X12               0.419
##     X13               0.625
##     X14               0.433
##     X15               0.602
##     X16               0.339
##     X17               0.048
##     X18               0.096
##     i2                0.024
##     X19               0.218
##     X20               0.177
##     X21               0.011
##     X22               0.336
##     X23               0.535
##     X24               0.421
##     X25               0.317
##     X26               0.326
##     X27               0.189
##     X28               0.233
##     X29               0.441
##     X30               0.557
##     p2                0.008
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{fitMeasures}\NormalTok{(model2.fit, }\DataTypeTok{fit.measures =} \StringTok{"aic"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##      aic 
## 16616.37
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{####mtmm participant word data 3####}
\NormalTok{model3 =}\StringTok{ '}
\StringTok{harmL =~ X1+X2+X3+X4+X5+X6+h3}
\StringTok{fairL =~ X7+X8+X9+X10+X11+X12+f3}
\StringTok{ingroupL =~ X13+X14+X15+X16+X17+X18+i3}
\StringTok{authorityL =~ X19+X20+X21+X22+X23+X24+a3}
\StringTok{purityL=~ X25+X26+X27+X28+X29+X30+p3}
\StringTok{mfq =~ X1+X2+X3+X4+X5+X6+X7+X8+X9+X10+X11+X12+X13+X14+X15+X16+X17+X18+X19+X20+X21+X22+X23+X24+X25+X26+X27+X28+X29+X30}
\StringTok{mfd =~ h3+f3+i3+a3+p3}

\StringTok{##fix the covariances}
\StringTok{harmL~~0*mfq}
\StringTok{fairL~~0*mfq}
\StringTok{ingroupL~~0*mfq}
\StringTok{authorityL~~0*mfq}
\StringTok{purityL~~0*mfq}
\StringTok{harmL~~0*mfd}
\StringTok{fairL~~0*mfd}
\StringTok{ingroupL~~0*mfd}
\StringTok{authorityL~~0*mfd}
\StringTok{purityL~~0*mfd}
\StringTok{h3~~.66*h3}
\StringTok{i3~~.56*i3}
\StringTok{f3~~1.97*f3}
\StringTok{'}

\NormalTok{model3.fit =}\StringTok{ }\KeywordTok{cfa}\NormalTok{(model3, }\DataTypeTok{data=}\NormalTok{mtmmdata, }\DataTypeTok{std.lv=}\OtherTok{TRUE}\NormalTok{)}
\KeywordTok{summary}\NormalTok{(model3.fit, }\DataTypeTok{rsquare=}\OtherTok{TRUE}\NormalTok{, }\DataTypeTok{standardized=}\OtherTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## lavaan (0.5-23.1097) converged normally after  64 iterations
## 
##   Number of observations                           160
## 
##   Estimator                                         ML
##   Minimum Function Test Statistic              925.997
##   Degrees of freedom                               517
##   P-value (Chi-square)                           0.000
## 
## Parameter Estimates:
## 
##   Information                                 Expected
##   Standard Errors                             Standard
## 
## Latent Variables:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   harmL =~                                                              
##     X1               -0.190    0.085   -2.224    0.026   -0.190   -0.183
##     X2               -0.033    0.095   -0.352    0.725   -0.033   -0.029
##     X3               -0.293    0.095   -3.087    0.002   -0.293   -0.278
##     X4                0.616    0.105    5.850    0.000    0.616    0.575
##     X5                0.379    0.088    4.311    0.000    0.379    0.352
##     X6                0.142    0.087    1.625    0.104    0.142    0.134
##     h3               -0.034    0.071   -0.483    0.629   -0.034   -0.042
##   fairL =~                                                              
##     X7                0.812    0.099    8.177    0.000    0.812    0.607
##     X8                0.868    0.081   10.671    0.000    0.868    0.694
##     X9                0.942    0.080   11.723    0.000    0.942    0.764
##     X10               0.987    0.084   11.790    0.000    0.987    0.792
##     X11               0.993    0.108    9.170    0.000    0.993    0.669
##     X12               0.594    0.084    7.028    0.000    0.594    0.509
##     f3                1.336    0.143    9.365    0.000    1.336    0.673
##   ingroupL =~                                                           
##     X13               1.067    0.100   10.685    0.000    1.067    0.760
##     X14               0.900    0.110    8.152    0.000    0.900    0.615
##     X15               1.429    0.130   11.001    0.000    1.429    0.781
##     X16               0.189    0.072    2.642    0.008    0.189    0.192
##     X17              -0.206    0.121   -1.702    0.089   -0.206   -0.143
##     X18               0.434    0.129    3.380    0.001    0.434    0.281
##     i3               -0.035    0.064   -0.550    0.582   -0.035   -0.047
##   authorityL =~                                                         
##     X19               0.195    0.105    1.858    0.063    0.195    0.154
##     X20               0.221    0.102    2.160    0.031    0.221    0.183
##     X21               0.030    0.133    0.222    0.824    0.030    0.020
##     X22               0.738    0.108    6.817    0.000    0.738    0.552
##     X23               1.020    0.111    9.157    0.000    1.020    0.718
##     X24               0.832    0.110    7.539    0.000    0.832    0.599
##     a3                0.032    0.066    0.487    0.626    0.032    0.043
##   purityL =~                                                            
##     X25               0.647    0.093    6.978    0.000    0.647    0.543
##     X26               0.810    0.113    7.138    0.000    0.810    0.540
##     X27               0.529    0.102    5.200    0.000    0.529    0.413
##     X28               0.672    0.115    5.845    0.000    0.672    0.466
##     X29               0.900    0.104    8.674    0.000    0.900    0.642
##     X30               1.210    0.119   10.207    0.000    1.210    0.736
##     p3                0.008    0.066    0.119    0.905    0.008    0.010
##   mfq =~                                                                
##     X1                0.795    0.073   10.878    0.000    0.795    0.766
##     X2                0.813    0.081   10.095    0.000    0.813    0.708
##     X3                0.940    0.071   13.298    0.000    0.940    0.889
##     X4                0.836    0.086    9.743    0.000    0.836    0.780
##     X5                0.803    0.080   10.023    0.000    0.803    0.747
##     X6                0.734    0.076    9.699    0.000    0.734    0.692
##     X7                0.189    0.108    1.753    0.080    0.189    0.141
##     X8                0.490    0.097    5.048    0.000    0.490    0.392
##     X9                0.375    0.097    3.858    0.000    0.375    0.304
##     X10               0.218    0.100    2.177    0.029    0.218    0.175
##     X11              -0.124    0.120   -1.034    0.301   -0.124   -0.084
##     X12               0.408    0.092    4.460    0.000    0.408    0.350
##     X13               0.190    0.115    1.663    0.096    0.190    0.136
##     X14               0.228    0.119    1.919    0.055    0.228    0.156
##     X15              -0.159    0.149   -1.066    0.286   -0.159   -0.087
##     X16               0.523    0.074    7.064    0.000    0.523    0.532
##     X17               0.235    0.116    2.021    0.043    0.235    0.163
##     X18               0.156    0.125    1.244    0.213    0.156    0.101
##     X19               0.464    0.099    4.674    0.000    0.464    0.367
##     X20               0.338    0.096    3.519    0.000    0.338    0.281
##     X21               0.064    0.122    0.525    0.599    0.064    0.043
##     X22              -0.211    0.109   -1.934    0.053   -0.211   -0.157
##     X23              -0.112    0.117   -0.959    0.338   -0.112   -0.079
##     X24              -0.249    0.113   -2.202    0.028   -0.249   -0.179
##     X25               0.049    0.098    0.498    0.618    0.049    0.041
##     X26              -0.364    0.121   -3.014    0.003   -0.364   -0.243
##     X27              -0.238    0.103   -2.296    0.022   -0.238   -0.186
##     X28               0.007    0.118    0.055    0.956    0.007    0.005
##     X29              -0.237    0.114   -2.079    0.038   -0.237   -0.169
##     X30              -0.073    0.135   -0.538    0.590   -0.073   -0.044
##   mfd =~                                                                
##     h3               -0.112    0.108   -1.044    0.297   -0.112   -0.137
##     f3                0.433    0.253    1.709    0.087    0.433    0.218
##     i3               -0.062    0.094   -0.658    0.511   -0.062   -0.082
##     a3               -0.066    0.095   -0.694    0.488   -0.066   -0.088
##     p3               -0.084    0.101   -0.833    0.405   -0.084   -0.107
## 
## Covariances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   harmL ~~                                                              
##     mfq               0.000                               0.000    0.000
##   fairL ~~                                                              
##     mfq               0.000                               0.000    0.000
##   ingroupL ~~                                                           
##     mfq               0.000                               0.000    0.000
##   authorityL ~~                                                         
##     mfq               0.000                               0.000    0.000
##   purityL ~~                                                            
##     mfq               0.000                               0.000    0.000
##   harmL ~~                                                              
##     mfd               0.000                               0.000    0.000
##   fairL ~~                                                              
##     mfd               0.000                               0.000    0.000
##   ingroupL ~~                                                           
##     mfd               0.000                               0.000    0.000
##   authorityL ~~                                                         
##     mfd               0.000                               0.000    0.000
##   purityL ~~                                                            
##     mfd               0.000                               0.000    0.000
##   harmL ~~                                                              
##     fairL            -0.059    0.095   -0.618    0.536   -0.059   -0.059
##     ingroupL         -0.167    0.096   -1.734    0.083   -0.167   -0.167
##     authorityL       -0.228    0.102   -2.226    0.026   -0.228   -0.228
##     purityL          -0.216    0.097   -2.220    0.026   -0.216   -0.216
##   fairL ~~                                                              
##     ingroupL          0.701    0.057   12.208    0.000    0.701    0.701
##     authorityL        0.486    0.085    5.731    0.000    0.486    0.486
##     purityL           0.540    0.074    7.256    0.000    0.540    0.540
##   ingroupL ~~                                                           
##     authorityL        0.525    0.088    5.981    0.000    0.525    0.525
##     purityL           0.832    0.052   16.031    0.000    0.832    0.832
##   authorityL ~~                                                         
##     purityL           0.876    0.059   14.974    0.000    0.876    0.876
##   mfq ~~                                                                
##     mfd               0.631    0.339    1.864    0.062    0.631    0.631
## 
## Variances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##    .h3                0.660                               0.660    0.980
##    .i3                0.560                               0.560    0.991
##    .f3                1.970                               1.970    0.500
##    .X1                0.410    0.058    7.040    0.000    0.410    0.380
##    .X2                0.656    0.079    8.290    0.000    0.656    0.497
##    .X3                0.148    0.058    2.559    0.011    0.148    0.132
##    .X4                0.070    0.092    0.760    0.448    0.070    0.061
##    .X5                0.366    0.061    6.041    0.000    0.366    0.317
##    .X6                0.567    0.067    8.467    0.000    0.567    0.504
##    .X7                1.093    0.132    8.295    0.000    1.093    0.611
##    .X8                0.572    0.077    7.470    0.000    0.572    0.365
##    .X9                0.491    0.070    6.970    0.000    0.491    0.323
##    .X10               0.533    0.077    6.954    0.000    0.533    0.343
##    .X11               1.201    0.150    7.984    0.000    1.201    0.546
##    .X12               0.841    0.099    8.463    0.000    0.841    0.618
##    .X13               0.799    0.120    6.666    0.000    0.799    0.405
##    .X14               1.276    0.160    7.958    0.000    1.276    0.597
##    .X15               1.285    0.202    6.363    0.000    1.285    0.383
##    .X16               0.658    0.076    8.653    0.000    0.658    0.680
##    .X17               1.978    0.222    8.896    0.000    1.978    0.953
##    .X18               2.171    0.246    8.810    0.000    2.171    0.911
##    .X19               1.347    0.153    8.784    0.000    1.347    0.842
##    .X20               1.292    0.147    8.800    0.000    1.292    0.888
##    .X21               2.256    0.252    8.942    0.000    2.256    0.998
##    .X22               1.201    0.153    7.846    0.000    1.201    0.671
##    .X23               0.963    0.157    6.148    0.000    0.963    0.478
##    .X24               1.173    0.157    7.495    0.000    1.173    0.609
##    .a3                0.556    0.063    8.832    0.000    0.556    0.990
##    .X25               0.997    0.119    8.362    0.000    0.997    0.703
##    .X26               1.464    0.176    8.303    0.000    1.464    0.650
##    .X27               1.303    0.151    8.643    0.000    1.303    0.795
##    .X28               1.626    0.190    8.567    0.000    1.626    0.783
##    .X29               1.099    0.139    7.898    0.000    1.099    0.559
##    .X30               1.230    0.171    7.180    0.000    1.230    0.456
##    .p3                0.602    0.069    8.773    0.000    0.602    0.988
##     harmL             1.000                               1.000    1.000
##     fairL             1.000                               1.000    1.000
##     ingroupL          1.000                               1.000    1.000
##     authorityL        1.000                               1.000    1.000
##     purityL           1.000                               1.000    1.000
##     mfq               1.000                               1.000    1.000
##     mfd               1.000                               1.000    1.000
## 
## R-Square:
##                    Estimate
##     h3                0.020
##     i3                0.009
##     f3                0.500
##     X1                0.620
##     X2                0.503
##     X3                0.868
##     X4                0.939
##     X5                0.683
##     X6                0.496
##     X7                0.389
##     X8                0.635
##     X9                0.677
##     X10               0.657
##     X11               0.454
##     X12               0.382
##     X13               0.595
##     X14               0.403
##     X15               0.617
##     X16               0.320
##     X17               0.047
##     X18               0.089
##     X19               0.158
##     X20               0.112
##     X21               0.002
##     X22               0.329
##     X23               0.522
##     X24               0.391
##     a3                0.010
##     X25               0.297
##     X26               0.350
##     X27               0.205
##     X28               0.217
##     X29               0.441
##     X30               0.544
##     p3                0.012
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{fitMeasures}\NormalTok{(model3.fit, }\DataTypeTok{fit.measures =} \StringTok{"aic"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##      aic 
## 16539.17
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{####mtmm model 1 and 2 together####}
\NormalTok{model4 =}\StringTok{ '}
\StringTok{harmL =~ X1+X2+X3+X4+X5+X6+h12}
\StringTok{fairL =~ X7+X8+X9+X10+X11+X12+f12}
\StringTok{ingroupL =~ X13+X14+X15+X16+X17+X18+i12}
\StringTok{authorityL =~ X19+X20+X21+X22+X23+X24+a12}
\StringTok{purityL=~ X25+X26+X27+X28+X29+X30+p12}
\StringTok{mfq =~ X1+X2+X3+X4+X5+X6+X7+X8+X9+X10+X11+X12+X13+X14+X15+X16+X17+X18+X19+X20+X21+X22+X23+X24+X25+X26+X27+X28+X29+X30}
\StringTok{mfd =~ h12+f12+i12+a12+p12}

\StringTok{##fix the covariances}
\StringTok{harmL~~0*mfq}
\StringTok{fairL~~0*mfq}
\StringTok{ingroupL~~0*mfq}
\StringTok{authorityL~~0*mfq}
\StringTok{purityL~~0*mfq}
\StringTok{harmL~~0*mfd}
\StringTok{fairL~~0*mfd}
\StringTok{ingroupL~~0*mfd}
\StringTok{authorityL~~0*mfd}
\StringTok{purityL~~0*mfd}
\StringTok{authorityL~~.5*purityL}
\StringTok{'}

\NormalTok{model4.fit =}\StringTok{ }\KeywordTok{cfa}\NormalTok{(model4, }\DataTypeTok{data=}\NormalTok{mtmmdata, }\DataTypeTok{std.lv=}\OtherTok{TRUE}\NormalTok{)}
\KeywordTok{summary}\NormalTok{(model4.fit, }\DataTypeTok{rsquare=}\OtherTok{TRUE}\NormalTok{, }\DataTypeTok{standardized=}\OtherTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## lavaan (0.5-23.1097) converged normally after  47 iterations
## 
##   Number of observations                           160
## 
##   Estimator                                         ML
##   Minimum Function Test Statistic              933.931
##   Degrees of freedom                               515
##   P-value (Chi-square)                           0.000
## 
## Parameter Estimates:
## 
##   Information                                 Expected
##   Standard Errors                             Standard
## 
## Latent Variables:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   harmL =~                                                              
##     X1                0.333    0.080    4.141    0.000    0.333    0.329
##     X2                0.300    0.091    3.316    0.001    0.300    0.267
##     X3                0.328    0.078    4.190    0.000    0.328    0.319
##     X4                0.647    0.077    8.349    0.000    0.647    0.631
##     X5                0.564    0.079    7.103    0.000    0.564    0.547
##     X6                0.662    0.079    8.424    0.000    0.662    0.650
##     h12               1.182    0.141    8.410    0.000    1.182    0.557
##   fairL =~                                                              
##     X7                0.766    0.103    7.427    0.000    0.766    0.561
##     X8                0.814    0.088    9.235    0.000    0.814    0.624
##     X9                0.887    0.085   10.422    0.000    0.887    0.691
##     X10               0.902    0.088   10.292    0.000    0.902    0.699
##     X11               0.991    0.113    8.803    0.000    0.991    0.664
##     X12               0.487    0.090    5.393    0.000    0.487    0.407
##     f12               1.268    0.123   10.283    0.000    1.268    0.632
##   ingroupL =~                                                           
##     X13               0.978    0.102    9.551    0.000    0.978    0.676
##     X14               0.815    0.114    7.161    0.000    0.815    0.547
##     X15               1.415    0.134   10.539    0.000    1.415    0.762
##     X16               0.019    0.077    0.241    0.810    0.019    0.019
##     X17              -0.305    0.122   -2.501    0.012   -0.305   -0.213
##     X18               0.312    0.130    2.406    0.016    0.312    0.201
##     i12               0.049    0.070    0.699    0.484    0.049    0.060
##   authorityL =~                                                         
##     X19               0.117    0.110    1.061    0.289    0.117    0.092
##     X20               0.153    0.106    1.439    0.150    0.153    0.126
##     X21               0.092    0.138    0.666    0.506    0.092    0.061
##     X22               0.732    0.113    6.465    0.000    0.732    0.555
##     X23               0.938    0.117    8.029    0.000    0.938    0.672
##     X24               0.834    0.116    7.198    0.000    0.834    0.612
##     a12               0.613    0.139    4.424    0.000    0.613    0.369
##   purityL =~                                                            
##     X25               0.548    0.095    5.756    0.000    0.548    0.462
##     X26               0.833    0.117    7.121    0.000    0.833    0.566
##     X27               0.539    0.105    5.145    0.000    0.539    0.426
##     X28               0.623    0.117    5.330    0.000    0.623    0.435
##     X29               0.924    0.104    8.877    0.000    0.924    0.674
##     X30               1.144    0.118    9.660    0.000    1.144    0.708
##     p12              -0.443    0.109   -4.070    0.000   -0.443   -0.342
##   mfq =~                                                                
##     X1                0.663    0.076    8.735    0.000    0.663    0.656
##     X2                0.751    0.084    8.894    0.000    0.751    0.669
##     X3                0.787    0.073   10.795    0.000    0.787    0.766
##     X4                0.495    0.079    6.258    0.000    0.495    0.483
##     X5                0.550    0.079    6.946    0.000    0.550    0.533
##     X6                0.407    0.081    5.046    0.000    0.407    0.400
##     X7                0.437    0.108    4.049    0.000    0.437    0.320
##     X8                0.662    0.095    6.956    0.000    0.662    0.508
##     X9                0.604    0.093    6.501    0.000    0.604    0.471
##     X10               0.539    0.095    5.663    0.000    0.539    0.417
##     X11               0.213    0.119    1.790    0.073    0.213    0.142
##     X12               0.576    0.094    6.153    0.000    0.576    0.481
##     X13               0.607    0.112    5.412    0.000    0.607    0.419
##     X14               0.509    0.120    4.232    0.000    0.509    0.342
##     X15               0.372    0.148    2.507    0.012    0.372    0.200
##     X16               0.601    0.077    7.789    0.000    0.601    0.609
##     X17               0.272    0.123    2.211    0.027    0.272    0.189
##     X18               0.496    0.130    3.800    0.000    0.496    0.319
##     X19               0.570    0.104    5.486    0.000    0.570    0.449
##     X20               0.486    0.100    4.858    0.000    0.486    0.402
##     X21               0.143    0.130    1.101    0.271    0.143    0.095
##     X22               0.100    0.111    0.907    0.365    0.100    0.076
##     X23               0.278    0.114    2.427    0.015    0.278    0.199
##     X24               0.081    0.114    0.716    0.474    0.081    0.060
##     X25               0.288    0.099    2.904    0.004    0.288    0.243
##     X26              -0.078    0.124   -0.629    0.529   -0.078   -0.053
##     X27              -0.084    0.108   -0.776    0.438   -0.084   -0.066
##     X28               0.275    0.121    2.272    0.023    0.275    0.192
##     X29               0.085    0.114    0.750    0.453    0.085    0.062
##     X30               0.365    0.132    2.775    0.006    0.365    0.226
##   mfd =~                                                                
##     h12               1.484    0.163    9.122    0.000    1.484    0.700
##     f12               1.412    0.145    9.756    0.000    1.412    0.704
##     i12              -0.096    0.072   -1.343    0.179   -0.096   -0.118
##     a12               0.729    0.133    5.495    0.000    0.729    0.438
##     p12               0.171    0.108    1.576    0.115    0.171    0.132
## 
## Covariances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   harmL ~~                                                              
##     mfq               0.000                               0.000    0.000
##   fairL ~~                                                              
##     mfq               0.000                               0.000    0.000
##   ingroupL ~~                                                           
##     mfq               0.000                               0.000    0.000
##   authorityL ~~                                                         
##     mfq               0.000                               0.000    0.000
##   purityL ~~                                                            
##     mfq               0.000                               0.000    0.000
##   harmL ~~                                                              
##     mfd               0.000                               0.000    0.000
##   fairL ~~                                                              
##     mfd               0.000                               0.000    0.000
##   ingroupL ~~                                                           
##     mfd               0.000                               0.000    0.000
##   authorityL ~~                                                         
##     mfd               0.000                               0.000    0.000
##   purityL ~~                                                            
##     mfd               0.000                               0.000    0.000
##   authorityL ~~                                                         
##     purityL           0.500                               0.500    0.500
##   harmL ~~                                                              
##     fairL            -0.063    0.114   -0.554    0.580   -0.063   -0.063
##     ingroupL         -0.345    0.112   -3.085    0.002   -0.345   -0.345
##     authorityL       -0.514    0.105   -4.892    0.000   -0.514   -0.514
##     purityL          -0.394    0.102   -3.882    0.000   -0.394   -0.394
##   fairL ~~                                                              
##     ingroupL          0.624    0.070    8.924    0.000    0.624    0.624
##     authorityL        0.246    0.099    2.490    0.013    0.246    0.246
##     purityL           0.425    0.087    4.871    0.000    0.425    0.425
##   ingroupL ~~                                                           
##     authorityL        0.218    0.088    2.495    0.013    0.218    0.218
##     purityL           0.819    0.056   14.543    0.000    0.819    0.819
##   mfq ~~                                                                
##     mfd               0.189    0.102    1.855    0.064    0.189    0.189
## 
## Variances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##    .X1                0.471    0.060    7.875    0.000    0.471    0.461
##    .X2                0.607    0.078    7.832    0.000    0.607    0.481
##    .X3                0.327    0.049    6.693    0.000    0.327    0.310
##    .X4                0.386    0.056    6.883    0.000    0.386    0.368
##    .X5                0.443    0.058    7.579    0.000    0.443    0.417
##    .X6                0.433    0.063    6.910    0.000    0.433    0.418
##    .h12               0.899    0.340    2.642    0.008    0.899    0.200
##    .X7                1.085    0.131    8.308    0.000    1.085    0.583
##    .X8                0.598    0.079    7.575    0.000    0.598    0.352
##    .X9                0.495    0.070    7.060    0.000    0.495    0.301
##    .X10               0.562    0.078    7.232    0.000    0.562    0.338
##    .X11               1.200    0.156    7.699    0.000    1.200    0.539
##    .X12               0.865    0.102    8.466    0.000    0.865    0.603
##    .f12               0.422    0.280    1.508    0.132    0.422    0.105
##    .X13               0.768    0.115    6.649    0.000    0.768    0.367
##    .X14               1.298    0.162    8.031    0.000    1.298    0.584
##    .X15               1.310    0.211    6.223    0.000    1.310    0.380
##    .X16               0.611    0.078    7.837    0.000    0.611    0.628
##    .X17               1.892    0.217    8.725    0.000    1.892    0.919
##    .X18               2.072    0.237    8.736    0.000    2.072    0.858
##    .i12               0.654    0.073    8.901    0.000    0.654    0.982
##    .X19               1.271    0.150    8.458    0.000    1.271    0.790
##    .X20               1.204    0.141    8.541    0.000    1.204    0.822
##    .X21               2.233    0.250    8.917    0.000    2.233    0.987
##    .X22               1.194    0.160    7.439    0.000    1.194    0.686
##    .X23               0.994    0.169    5.888    0.000    0.994    0.509
##    .X24               1.154    0.167    6.904    0.000    1.154    0.622
##    .a12               1.858    0.243    7.659    0.000    1.858    0.672
##    .X25               1.023    0.122    8.367    0.000    1.023    0.727
##    .X26               1.464    0.184    7.959    0.000    1.464    0.676
##    .X27               1.302    0.154    8.464    0.000    1.302    0.814
##    .X28               1.592    0.188    8.483    0.000    1.592    0.774
##    .X29               1.016    0.139    7.331    0.000    1.016    0.541
##    .X30               1.166    0.171    6.813    0.000    1.166    0.447
##    .p12               1.453    0.169    8.616    0.000    1.453    0.866
##     harmL             1.000                               1.000    1.000
##     fairL             1.000                               1.000    1.000
##     ingroupL          1.000                               1.000    1.000
##     authorityL        1.000                               1.000    1.000
##     purityL           1.000                               1.000    1.000
##     mfq               1.000                               1.000    1.000
##     mfd               1.000                               1.000    1.000
## 
## R-Square:
##                    Estimate
##     X1                0.539
##     X2                0.519
##     X3                0.690
##     X4                0.632
##     X5                0.583
##     X6                0.582
##     h12               0.800
##     X7                0.417
##     X8                0.648
##     X9                0.699
##     X10               0.662
##     X11               0.461
##     X12               0.397
##     f12               0.895
##     X13               0.633
##     X14               0.416
##     X15               0.620
##     X16               0.372
##     X17               0.081
##     X18               0.142
##     i12               0.018
##     X19               0.210
##     X20               0.178
##     X21               0.013
##     X22               0.314
##     X23               0.491
##     X24               0.378
##     a12               0.328
##     X25               0.273
##     X26               0.324
##     X27               0.186
##     X28               0.226
##     X29               0.459
##     X30               0.553
##     p12               0.134
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{fitMeasures}\NormalTok{(model4.fit, }\DataTypeTok{fit.measures =} \StringTok{"aic"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##      aic 
## 17328.55
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{####mtmm model 2 and 3 together####}
\NormalTok{model5 =}\StringTok{ '}
\StringTok{harmL =~ X1+X2+X3+X4+X5+X6+h23}
\StringTok{fairL =~ X7+X8+X9+X10+X11+X12+f23}
\StringTok{ingroupL =~ X13+X14+X15+X16+X17+X18+i23}
\StringTok{authorityL =~ X19+X20+X21+X22+X23+X24+a23}
\StringTok{purityL=~ X25+X26+X27+X28+X29+X30+p23}
\StringTok{mfq =~ X1+X2+X3+X4+X5+X6+X7+X8+X9+X10+X11+X12+X13+X14+X15+X16+X17+X18+X19+X20+X21+X22+X23+X24+X25+X26+X27+X28+X29+X30}
\StringTok{mfd =~ h23+f23+i23+a23+p23}

\StringTok{##fix the covariances}
\StringTok{harmL~~0*mfq}
\StringTok{fairL~~0*mfq}
\StringTok{ingroupL~~0*mfq}
\StringTok{authorityL~~0*mfq}
\StringTok{purityL~~0*mfq}
\StringTok{harmL~~0*mfd}
\StringTok{fairL~~0*mfd}
\StringTok{ingroupL~~0*mfd}
\StringTok{authorityL~~0*mfd}
\StringTok{purityL~~0*mfd}
\StringTok{h23~~2.07*h23}
\StringTok{a23~~1.70*a23}
\StringTok{'}

\NormalTok{model5.fit =}\StringTok{ }\KeywordTok{cfa}\NormalTok{(model5, }\DataTypeTok{data=}\NormalTok{mtmmdata, }\DataTypeTok{std.lv=}\OtherTok{TRUE}\NormalTok{)}
\KeywordTok{summary}\NormalTok{(model5.fit, }\DataTypeTok{rsquare=}\OtherTok{TRUE}\NormalTok{, }\DataTypeTok{standardized=}\OtherTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## lavaan (0.5-23.1097) converged normally after  59 iterations
## 
##   Number of observations                           160
## 
##   Estimator                                         ML
##   Minimum Function Test Statistic              988.958
##   Degrees of freedom                               516
##   P-value (Chi-square)                           0.000
## 
## Parameter Estimates:
## 
##   Information                                 Expected
##   Standard Errors                             Standard
## 
## Latent Variables:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   harmL =~                                                              
##     X1               -0.123    0.083   -1.493    0.135   -0.123   -0.118
##     X2                0.028    0.092    0.310    0.757    0.028    0.025
##     X3               -0.191    0.086   -2.212    0.027   -0.191   -0.178
##     X4                0.691    0.096    7.230    0.000    0.691    0.674
##     X5                0.446    0.085    5.263    0.000    0.446    0.427
##     X6                0.208    0.084    2.465    0.014    0.208    0.198
##     h23               0.260    0.156    1.662    0.096    0.260    0.119
##   fairL =~                                                              
##     X7                0.842    0.099    8.472    0.000    0.842    0.600
##     X8                0.898    0.082   10.902    0.000    0.898    0.649
##     X9                0.958    0.082   11.692    0.000    0.958    0.705
##     X10               0.994    0.085   11.654    0.000    0.994    0.737
##     X11               1.038    0.108    9.607    0.000    1.038    0.686
##     X12               0.624    0.084    7.410    0.000    0.624    0.500
##     f23               1.686    0.123   13.720    0.000    1.686    0.750
##   ingroupL =~                                                           
##     X13               1.086    0.101   10.757    0.000    1.086    0.733
##     X14               0.915    0.111    8.216    0.000    0.915    0.601
##     X15               1.465    0.131   11.169    0.000    1.465    0.785
##     X16               0.178    0.072    2.473    0.013    0.178    0.177
##     X17              -0.226    0.121   -1.869    0.062   -0.226   -0.157
##     X18               0.441    0.129    3.427    0.001    0.441    0.282
##     i23               0.028    0.057    0.495    0.621    0.028    0.042
##   authorityL =~                                                         
##     X19               0.275    0.103    2.687    0.007    0.275    0.213
##     X20               0.291    0.100    2.908    0.004    0.291    0.236
##     X21               0.111    0.131    0.845    0.398    0.111    0.074
##     X22               0.784    0.106    7.372    0.000    0.784    0.585
##     X23               1.072    0.108    9.931    0.000    1.072    0.735
##     X24               0.916    0.107    8.540    0.000    0.916    0.660
##     a23               1.156    0.138    8.392    0.000    1.156    0.576
##   purityL =~                                                            
##     X25               0.661    0.093    7.083    0.000    0.661    0.540
##     X26               0.839    0.114    7.362    0.000    0.839    0.566
##     X27               0.547    0.102    5.364    0.000    0.547    0.430
##     X28               0.707    0.115    6.145    0.000    0.707    0.483
##     X29               0.941    0.104    9.040    0.000    0.941    0.670
##     X30               1.243    0.120   10.360    0.000    1.243    0.735
##     p23               0.030    0.079    0.378    0.706    0.030    0.032
##   mfq =~                                                                
##     X1                0.825    0.072   11.533    0.000    0.825    0.788
##     X2                0.820    0.081   10.185    0.000    0.820    0.715
##     X3                0.966    0.069   13.990    0.000    0.966    0.899
##     X4                0.710    0.085    8.342    0.000    0.710    0.692
##     X5                0.727    0.079    9.157    0.000    0.727    0.697
##     X6                0.701    0.076    9.193    0.000    0.701    0.669
##     X7                0.420    0.102    4.128    0.000    0.420    0.299
##     X8                0.743    0.091    8.136    0.000    0.743    0.536
##     X9                0.649    0.089    7.268    0.000    0.649    0.477
##     X10               0.515    0.090    5.710    0.000    0.515    0.381
##     X11               0.176    0.109    1.614    0.107    0.176    0.116
##     X12               0.595    0.089    6.669    0.000    0.595    0.477
##     X13               0.468    0.110    4.245    0.000    0.468    0.316
##     X14               0.445    0.116    3.825    0.000    0.445    0.293
##     X15               0.214    0.141    1.520    0.129    0.214    0.115
##     X16               0.569    0.075    7.591    0.000    0.569    0.566
##     X17               0.195    0.116    1.675    0.094    0.195    0.136
##     X18               0.273    0.126    2.174    0.030    0.273    0.175
##     X19               0.549    0.100    5.473    0.000    0.549    0.424
##     X20               0.441    0.097    4.556    0.000    0.441    0.358
##     X21               0.091    0.123    0.742    0.458    0.091    0.061
##     X22               0.017    0.104    0.161    0.872    0.017    0.013
##     X23               0.204    0.109    1.870    0.061    0.204    0.140
##     X24               0.009    0.106    0.089    0.929    0.009    0.007
##     X25               0.246    0.096    2.569    0.010    0.246    0.201
##     X26              -0.133    0.117   -1.142    0.253   -0.133   -0.090
##     X27              -0.086    0.102   -0.843    0.399   -0.086   -0.068
##     X28               0.198    0.116    1.703    0.089    0.198    0.135
##     X29               0.023    0.109    0.208    0.836    0.023    0.016
##     X30               0.270    0.129    2.087    0.037    0.270    0.160
##   mfd =~                                                                
##     h23               1.621    0.156   10.370    0.000    1.621    0.743
##     f23               1.463    0.129   11.311    0.000    1.463    0.651
##     i23               0.002    0.056    0.028    0.977    0.002    0.002
##     a23               0.995    0.138    7.186    0.000    0.995    0.496
##     p23              -0.024    0.079   -0.302    0.762   -0.024   -0.026
## 
## Covariances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   harmL ~~                                                              
##     mfq               0.000                               0.000    0.000
##   fairL ~~                                                              
##     mfq               0.000                               0.000    0.000
##   ingroupL ~~                                                           
##     mfq               0.000                               0.000    0.000
##   authorityL ~~                                                         
##     mfq               0.000                               0.000    0.000
##   purityL ~~                                                            
##     mfq               0.000                               0.000    0.000
##   harmL ~~                                                              
##     mfd               0.000                               0.000    0.000
##   fairL ~~                                                              
##     mfd               0.000                               0.000    0.000
##   ingroupL ~~                                                           
##     mfd               0.000                               0.000    0.000
##   authorityL ~~                                                         
##     mfd               0.000                               0.000    0.000
##   purityL ~~                                                            
##     mfd               0.000                               0.000    0.000
##   harmL ~~                                                              
##     fairL            -0.076    0.099   -0.767    0.443   -0.076   -0.076
##     ingroupL         -0.191    0.098   -1.943    0.052   -0.191   -0.191
##     authorityL       -0.230    0.098   -2.358    0.018   -0.230   -0.230
##     purityL          -0.255    0.095   -2.683    0.007   -0.255   -0.255
##   fairL ~~                                                              
##     ingroupL          0.703    0.055   12.695    0.000    0.703    0.703
##     authorityL        0.464    0.078    5.926    0.000    0.464    0.464
##     purityL           0.548    0.072    7.629    0.000    0.548    0.548
##   ingroupL ~~                                                           
##     authorityL        0.503    0.082    6.121    0.000    0.503    0.503
##     purityL           0.840    0.050   16.920    0.000    0.840    0.840
##   authorityL ~~                                                         
##     purityL           0.820    0.054   15.330    0.000    0.820    0.820
##   mfq ~~                                                                
##     mfd               0.492    0.078    6.321    0.000    0.492    0.492
## 
## Variances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##    .h23               2.070                               2.070    0.434
##    .a23               1.700                               1.700    0.422
##    .X1                0.401    0.056    7.141    0.000    0.401    0.365
##    .X2                0.641    0.078    8.233    0.000    0.641    0.488
##    .X3                0.184    0.050    3.676    0.000    0.184    0.159
##    .X4                0.071    0.094    0.754    0.451    0.071    0.067
##    .X5                0.362    0.060    6.002    0.000    0.362    0.332
##    .X6                0.562    0.067    8.445    0.000    0.562    0.513
##    .X7                1.086    0.129    8.426    0.000    1.086    0.551
##    .X8                0.559    0.073    7.680    0.000    0.559    0.291
##    .X9                0.507    0.068    7.445    0.000    0.507    0.275
##    .X10               0.569    0.075    7.543    0.000    0.569    0.312
##    .X11               1.182    0.145    8.153    0.000    1.182    0.516
##    .X12               0.814    0.096    8.499    0.000    0.814    0.523
##    .f23               0.072    0.175    0.412    0.680    0.072    0.014
##    .X13               0.797    0.119    6.699    0.000    0.797    0.363
##    .X14               1.282    0.161    7.982    0.000    1.282    0.553
##    .X15               1.290    0.203    6.368    0.000    1.290    0.370
##    .X16               0.657    0.076    8.608    0.000    0.657    0.649
##    .X17               1.967    0.221    8.883    0.000    1.967    0.957
##    .X18               2.168    0.246    8.812    0.000    2.168    0.890
##    .i23               0.439    0.049    8.942    0.000    0.439    0.998
##    .X19               1.300    0.149    8.707    0.000    1.300    0.775
##    .X20               1.242    0.142    8.734    0.000    1.242    0.817
##    .X21               2.246    0.251    8.932    0.000    2.246    0.991
##    .X22               1.181    0.149    7.899    0.000    1.181    0.658
##    .X23               0.934    0.144    6.464    0.000    0.934    0.440
##    .X24               1.090    0.148    7.383    0.000    1.090    0.565
##    .X25               1.000    0.120    8.364    0.000    1.000    0.668
##    .X26               1.473    0.178    8.276    0.000    1.473    0.671
##    .X27               1.309    0.152    8.631    0.000    1.309    0.810
##    .X28               1.606    0.188    8.540    0.000    1.606    0.749
##    .X29               1.086    0.139    7.826    0.000    1.086    0.551
##    .X30               1.243    0.173    7.195    0.000    1.243    0.435
##    .p23               0.864    0.097    8.942    0.000    0.864    0.998
##     harmL             1.000                               1.000    1.000
##     fairL             1.000                               1.000    1.000
##     ingroupL          1.000                               1.000    1.000
##     authorityL        1.000                               1.000    1.000
##     purityL           1.000                               1.000    1.000
##     mfq               1.000                               1.000    1.000
##     mfd               1.000                               1.000    1.000
## 
## R-Square:
##                    Estimate
##     h23               0.566
##     a23               0.578
##     X1                0.635
##     X2                0.512
##     X3                0.841
##     X4                0.933
##     X5                0.668
##     X6                0.487
##     X7                0.449
##     X8                0.709
##     X9                0.725
##     X10               0.688
##     X11               0.484
##     X12               0.477
##     f23               0.986
##     X13               0.637
##     X14               0.447
##     X15               0.630
##     X16               0.351
##     X17               0.043
##     X18               0.110
##     i23               0.002
##     X19               0.225
##     X20               0.183
##     X21               0.009
##     X22               0.342
##     X23               0.560
##     X24               0.435
##     X25               0.332
##     X26               0.329
##     X27               0.190
##     X28               0.251
##     X29               0.449
##     X30               0.565
##     p23               0.002
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{fitMeasures}\NormalTok{(model5.fit, }\DataTypeTok{fit.measures =} \StringTok{"aic"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##      aic 
## 17043.75
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{####mtmm model 1 2 and 3 together####}
\NormalTok{model6 =}\StringTok{ '}
\StringTok{harmL =~ X1+X2+X3+X4+X5+X6+h123}
\StringTok{fairL =~ X7+X8+X9+X10+X11+X12+f123}
\StringTok{ingroupL =~ X13+X14+X15+X16+X17+X18+i123}
\StringTok{authorityL =~ X19+X20+X21+X22+X23+X24+a123}
\StringTok{purityL=~ X25+X26+X27+X28+X29+X30+p123}
\StringTok{mfq =~ X1+X2+X3+X4+X5+X6+X7+X8+X9+X10+X11+X12+X13+X14+X15+X16+X17+X18+X19+X20+X21+X22+X23+X24+X25+X26+X27+X28+X29+X30}
\StringTok{mfd =~ h123+f123+i123+a123+p123}

\StringTok{##fix the covariances}
\StringTok{harmL~~0*mfq}
\StringTok{fairL~~0*mfq}
\StringTok{ingroupL~~0*mfq}
\StringTok{authorityL~~0*mfq}
\StringTok{purityL~~0*mfq}
\StringTok{harmL~~0*mfd}
\StringTok{fairL~~0*mfd}
\StringTok{ingroupL~~0*mfd}
\StringTok{authorityL~~0*mfd}
\StringTok{purityL~~0*mfd}
\StringTok{authorityL~~.80*purityL}
\StringTok{'}

\NormalTok{model6.fit =}\StringTok{ }\KeywordTok{cfa}\NormalTok{(model6, }\DataTypeTok{data=}\NormalTok{mtmmdata, }\DataTypeTok{std.lv=}\OtherTok{TRUE}\NormalTok{)}
\KeywordTok{summary}\NormalTok{(model6.fit, }\DataTypeTok{rsquare=}\OtherTok{TRUE}\NormalTok{, }\DataTypeTok{standardized=}\OtherTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## lavaan (0.5-23.1097) converged normally after  44 iterations
## 
##   Number of observations                           160
## 
##   Estimator                                         ML
##   Minimum Function Test Statistic              900.438
##   Degrees of freedom                               515
##   P-value (Chi-square)                           0.000
## 
## Parameter Estimates:
## 
##   Information                                 Expected
##   Standard Errors                             Standard
## 
## Latent Variables:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   harmL =~                                                              
##     X1                0.360    0.083    4.357    0.000    0.360    0.354
##     X2                0.288    0.094    3.075    0.002    0.288    0.255
##     X3                0.349    0.082    4.266    0.000    0.349    0.337
##     X4                0.618    0.080    7.699    0.000    0.618    0.594
##     X5                0.535    0.082    6.504    0.000    0.535    0.512
##     X6                0.679    0.080    8.493    0.000    0.679    0.657
##     h123              1.166    0.150    7.791    0.000    1.166    0.560
##   fairL =~                                                              
##     X7                0.761    0.104    7.343    0.000    0.761    0.558
##     X8                0.827    0.088    9.362    0.000    0.827    0.636
##     X9                0.896    0.085   10.488    0.000    0.896    0.699
##     X10               0.904    0.088   10.231    0.000    0.904    0.702
##     X11               0.982    0.113    8.661    0.000    0.982    0.657
##     X12               0.496    0.091    5.460    0.000    0.496    0.415
##     f123              1.293    0.134    9.653    0.000    1.293    0.642
##   ingroupL =~                                                           
##     X13               0.972    0.104    9.367    0.000    0.972    0.675
##     X14               0.814    0.115    7.099    0.000    0.814    0.547
##     X15               1.410    0.135   10.469    0.000    1.410    0.760
##     X16               0.017    0.079    0.214    0.831    0.017    0.017
##     X17              -0.310    0.122   -2.529    0.011   -0.310   -0.216
##     X18               0.305    0.130    2.341    0.019    0.305    0.196
##     i123              0.031    0.086    0.362    0.717    0.031    0.031
##   authorityL =~                                                         
##     X19               0.051    0.107    0.478    0.633    0.051    0.040
##     X20               0.105    0.103    1.019    0.308    0.105    0.087
##     X21               0.081    0.132    0.611    0.541    0.081    0.054
##     X22               0.748    0.108    6.915    0.000    0.748    0.560
##     X23               0.981    0.110    8.883    0.000    0.981    0.688
##     X24               0.873    0.110    7.951    0.000    0.873    0.630
##     a123              0.612    0.146    4.187    0.000    0.612    0.343
##   purityL =~                                                            
##     X25               0.577    0.094    6.105    0.000    0.577    0.482
##     X26               0.887    0.115    7.699    0.000    0.887    0.596
##     X27               0.591    0.103    5.744    0.000    0.591    0.464
##     X28               0.635    0.116    5.469    0.000    0.635    0.439
##     X29               0.944    0.104    9.071    0.000    0.944    0.676
##     X30               1.156    0.120    9.655    0.000    1.156    0.700
##     p123             -0.459    0.122   -3.766    0.000   -0.459   -0.314
##   mfq =~                                                                
##     X1                0.659    0.077    8.569    0.000    0.659    0.648
##     X2                0.767    0.085    9.029    0.000    0.767    0.679
##     X3                0.784    0.074   10.578    0.000    0.784    0.758
##     X4                0.537    0.081    6.594    0.000    0.537    0.516
##     X5                0.589    0.081    7.277    0.000    0.589    0.563
##     X6                0.426    0.083    5.117    0.000    0.426    0.412
##     X7                0.434    0.108    4.026    0.000    0.434    0.318
##     X8                0.658    0.095    6.945    0.000    0.658    0.505
##     X9                0.601    0.093    6.491    0.000    0.601    0.469
##     X10               0.520    0.095    5.457    0.000    0.520    0.403
##     X11               0.194    0.119    1.632    0.103    0.194    0.130
##     X12               0.562    0.093    6.021    0.000    0.562    0.471
##     X13               0.597    0.114    5.236    0.000    0.597    0.414
##     X14               0.504    0.121    4.151    0.000    0.504    0.339
##     X15               0.368    0.151    2.433    0.015    0.368    0.198
##     X16               0.602    0.077    7.832    0.000    0.602    0.611
##     X17               0.266    0.123    2.169    0.030    0.266    0.185
##     X18               0.508    0.130    3.901    0.000    0.508    0.327
##     X19               0.570    0.104    5.502    0.000    0.570    0.450
##     X20               0.485    0.100    4.852    0.000    0.485    0.401
##     X21               0.150    0.130    1.156    0.248    0.150    0.100
##     X22               0.133    0.112    1.192    0.233    0.133    0.100
##     X23               0.327    0.116    2.831    0.005    0.327    0.230
##     X24               0.127    0.115    1.107    0.268    0.127    0.092
##     X25               0.298    0.100    2.978    0.003    0.298    0.249
##     X26              -0.050    0.125   -0.396    0.692   -0.050   -0.033
##     X27              -0.055    0.108   -0.508    0.611   -0.055   -0.043
##     X28               0.304    0.122    2.494    0.013    0.304    0.210
##     X29               0.113    0.116    0.975    0.330    0.113    0.081
##     X30               0.386    0.135    2.859    0.004    0.386    0.234
##   mfd =~                                                                
##     h123              1.543    0.187    8.231    0.000    1.543    0.741
##     f123              1.150    0.158    7.282    0.000    1.150    0.571
##     i123             -0.090    0.090   -0.996    0.319   -0.090   -0.090
##     a123              0.767    0.151    5.085    0.000    0.767    0.430
##     p123             -0.077    0.127   -0.609    0.542   -0.077   -0.053
## 
## Covariances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   harmL ~~                                                              
##     mfq               0.000                               0.000    0.000
##   fairL ~~                                                              
##     mfq               0.000                               0.000    0.000
##   ingroupL ~~                                                           
##     mfq               0.000                               0.000    0.000
##   authorityL ~~                                                         
##     mfq               0.000                               0.000    0.000
##   purityL ~~                                                            
##     mfq               0.000                               0.000    0.000
##   harmL ~~                                                              
##     mfd               0.000                               0.000    0.000
##   fairL ~~                                                              
##     mfd               0.000                               0.000    0.000
##   ingroupL ~~                                                           
##     mfd               0.000                               0.000    0.000
##   authorityL ~~                                                         
##     mfd               0.000                               0.000    0.000
##   purityL ~~                                                            
##     mfd               0.000                               0.000    0.000
##   authorityL ~~                                                         
##     purityL           0.800                               0.800    0.800
##   harmL ~~                                                              
##     fairL            -0.116    0.117   -0.998    0.318   -0.116   -0.116
##     ingroupL         -0.417    0.113   -3.696    0.000   -0.417   -0.417
##     authorityL       -0.643    0.101   -6.384    0.000   -0.643   -0.643
##     purityL          -0.509    0.100   -5.112    0.000   -0.509   -0.509
##   fairL ~~                                                              
##     ingroupL          0.633    0.070    9.043    0.000    0.633    0.633
##     authorityL        0.330    0.097    3.398    0.001    0.330    0.330
##     purityL           0.437    0.087    5.016    0.000    0.437    0.437
##   ingroupL ~~                                                           
##     authorityL        0.418    0.086    4.873    0.000    0.418    0.418
##     purityL           0.810    0.057   14.200    0.000    0.810    0.810
##   mfq ~~                                                                
##     mfd               0.232    0.102    2.279    0.023    0.232    0.232
## 
## Variances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##    .X1                0.471    0.060    7.900    0.000    0.471    0.455
##    .X2                0.607    0.078    7.788    0.000    0.607    0.475
##    .X3                0.333    0.049    6.828    0.000    0.333    0.312
##    .X4                0.413    0.057    7.190    0.000    0.413    0.381
##    .X5                0.460    0.060    7.695    0.000    0.460    0.421
##    .X6                0.425    0.063    6.754    0.000    0.425    0.398
##    .h123              0.592    0.447    1.324    0.186    0.592    0.137
##    .X7                1.094    0.132    8.308    0.000    1.094    0.588
##    .X8                0.577    0.077    7.450    0.000    0.577    0.341
##    .X9                0.480    0.069    6.911    0.000    0.480    0.292
##    .X10               0.573    0.079    7.207    0.000    0.573    0.345
##    .X11               1.233    0.160    7.730    0.000    1.233    0.552
##    .X12               0.865    0.102    8.469    0.000    0.865    0.606
##    .f123              1.066    0.280    3.812    0.000    1.066    0.262
##    .X13               0.776    0.117    6.658    0.000    0.776    0.374
##    .X14               1.296    0.162    8.014    0.000    1.296    0.586
##    .X15               1.314    0.212    6.195    0.000    1.314    0.382
##    .X16               0.609    0.078    7.850    0.000    0.609    0.626
##    .X17               1.893    0.217    8.729    0.000    1.893    0.919
##    .X18               2.061    0.236    8.729    0.000    2.061    0.855
##    .i123              0.989    0.111    8.919    0.000    0.989    0.991
##    .X19               1.279    0.151    8.492    0.000    1.279    0.796
##    .X20               1.217    0.142    8.586    0.000    1.217    0.832
##    .X21               2.234    0.250    8.921    0.000    2.234    0.987
##    .X22               1.210    0.153    7.889    0.000    1.210    0.677
##    .X23               0.966    0.148    6.510    0.000    0.966    0.475
##    .X24               1.140    0.154    7.408    0.000    1.140    0.594
##    .a123              2.216    0.288    7.699    0.000    2.216    0.697
##    .X25               1.013    0.120    8.428    0.000    1.013    0.706
##    .X26               1.428    0.178    8.006    0.000    1.428    0.644
##    .X27               1.270    0.150    8.468    0.000    1.270    0.783
##    .X28               1.598    0.187    8.557    0.000    1.598    0.763
##    .X29               1.047    0.137    7.616    0.000    1.047    0.537
##    .X30               1.239    0.170    7.282    0.000    1.239    0.455
##    .p123              1.917    0.219    8.772    0.000    1.917    0.899
##     harmL             1.000                               1.000    1.000
##     fairL             1.000                               1.000    1.000
##     ingroupL          1.000                               1.000    1.000
##     authorityL        1.000                               1.000    1.000
##     purityL           1.000                               1.000    1.000
##     mfq               1.000                               1.000    1.000
##     mfd               1.000                               1.000    1.000
## 
## R-Square:
##                    Estimate
##     X1                0.545
##     X2                0.525
##     X3                0.688
##     X4                0.619
##     X5                0.579
##     X6                0.602
##     h123              0.863
##     X7                0.412
##     X8                0.659
##     X9                0.708
##     X10               0.655
##     X11               0.448
##     X12               0.394
##     f123              0.738
##     X13               0.626
##     X14               0.414
##     X15               0.618
##     X16               0.374
##     X17               0.081
##     X18               0.145
##     i123              0.009
##     X19               0.204
##     X20               0.168
##     X21               0.013
##     X22               0.323
##     X23               0.525
##     X24               0.406
##     a123              0.303
##     X25               0.294
##     X26               0.356
##     X27               0.217
##     X28               0.237
##     X29               0.463
##     X30               0.545
##     p123              0.101
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{fitMeasures}\NormalTok{(model6.fit, }\DataTypeTok{fit.measures =} \StringTok{"aic"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##      aic 
## 17465.16
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{####focus on final model####}
\NormalTok{##traits only model}
\NormalTok{model6.}\DecValTok{1}\NormalTok{ =}\StringTok{ '}
\StringTok{harmL =~ X1+X2+X3+X4+X5+X6+h123}
\StringTok{fairL =~ X7+X8+X9+X10+X11+X12+f123}
\StringTok{ingroupL =~ X13+X14+X15+X16+X17+X18+i123}
\StringTok{authorityL =~ X19+X20+X21+X22+X23+X24+a123}
\StringTok{purityL=~ X25+X26+X27+X28+X29+X30+p123}
\StringTok{'}
\NormalTok{model6.}\FloatTok{1.}\NormalTok{fit =}\StringTok{ }\KeywordTok{cfa}\NormalTok{(model6.}\DecValTok{1}\NormalTok{, }\DataTypeTok{data=}\NormalTok{mtmmdata, }\DataTypeTok{std.lv=}\OtherTok{TRUE}\NormalTok{)}
\KeywordTok{summary}\NormalTok{(model6.}\FloatTok{1.}\NormalTok{fit, }\DataTypeTok{rsquare=}\OtherTok{TRUE}\NormalTok{, }\DataTypeTok{standardized=}\OtherTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## lavaan (0.5-23.1097) converged normally after  33 iterations
## 
##   Number of observations                           160
## 
##   Estimator                                         ML
##   Minimum Function Test Statistic             1204.242
##   Degrees of freedom                               550
##   P-value (Chi-square)                           0.000
## 
## Parameter Estimates:
## 
##   Information                                 Expected
##   Standard Errors                             Standard
## 
## Latent Variables:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   harmL =~                                                              
##     X1                0.763    0.073   10.430    0.000    0.763    0.735
##     X2                0.790    0.083    9.535    0.000    0.790    0.688
##     X3                0.829    0.072   11.450    0.000    0.829    0.784
##     X4                0.863    0.072   11.926    0.000    0.863    0.806
##     X5                0.855    0.073   11.719    0.000    0.855    0.797
##     X6                0.777    0.075   10.389    0.000    0.777    0.733
##     h123              1.130    0.164    6.874    0.000    1.130    0.528
##   fairL =~                                                              
##     X7                0.825    0.100    8.264    0.000    0.825    0.617
##     X8                1.004    0.086   11.747    0.000    1.004    0.800
##     X9                1.038    0.082   12.640    0.000    1.038    0.840
##     X10               0.991    0.085   11.600    0.000    0.991    0.793
##     X11               0.851    0.112    7.566    0.000    0.851    0.574
##     X12               0.678    0.088    7.665    0.000    0.678    0.580
##     f123              0.867    0.144    6.013    0.000    0.867    0.471
##   ingroupL =~                                                           
##     X13               1.105    0.100   11.011    0.000    1.105    0.786
##     X14               0.936    0.111    8.408    0.000    0.936    0.639
##     X15               1.354    0.133   10.158    0.000    1.354    0.740
##     X16               0.246    0.083    2.965    0.003    0.246    0.250
##     X17              -0.167    0.123   -1.355    0.176   -0.167   -0.116
##     X18               0.447    0.129    3.454    0.001    0.447    0.289
##     i123              0.042    0.086    0.487    0.626    0.042    0.042
##   authorityL =~                                                         
##     X19               0.083    0.112    0.747    0.455    0.083    0.066
##     X20               0.134    0.106    1.262    0.207    0.134    0.111
##     X21               0.042    0.133    0.317    0.751    0.042    0.028
##     X22               0.763    0.109    7.033    0.000    0.763    0.571
##     X23               1.006    0.111    9.072    0.000    1.006    0.709
##     X24               0.882    0.110    7.986    0.000    0.882    0.635
##     a123              0.440    0.152    2.899    0.004    0.440    0.252
##   purityL =~                                                            
##     X25               0.620    0.093    6.634    0.000    0.620    0.521
##     X26               0.858    0.116    7.411    0.000    0.858    0.572
##     X27               0.569    0.103    5.544    0.000    0.569    0.445
##     X28               0.679    0.115    5.917    0.000    0.679    0.471
##     X29               0.935    0.104    8.973    0.000    0.935    0.667
##     X30               1.190    0.119    9.990    0.000    1.190    0.725
##     p123             -0.453    0.120   -3.767    0.000   -0.453   -0.311
## 
## Covariances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   harmL ~~                                                              
##     fairL             0.318    0.081    3.941    0.000    0.318    0.318
##     ingroupL          0.086    0.093    0.915    0.360    0.086    0.086
##     authorityL       -0.249    0.096   -2.604    0.009   -0.249   -0.249
##     purityL          -0.211    0.091   -2.312    0.021   -0.211   -0.211
##   fairL ~~                                                              
##     ingroupL          0.696    0.058   11.991    0.000    0.696    0.696
##     authorityL        0.402    0.089    4.516    0.000    0.402    0.402
##     purityL           0.460    0.079    5.803    0.000    0.460    0.460
##   ingroupL ~~                                                           
##     authorityL        0.484    0.090    5.367    0.000    0.484    0.484
##     purityL           0.788    0.056   14.001    0.000    0.788    0.788
##   authorityL ~~                                                         
##     purityL           0.876    0.057   15.424    0.000    0.876    0.876
## 
## Variances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##    .X1                0.496    0.064    7.776    0.000    0.496    0.460
##    .X2                0.695    0.086    8.053    0.000    0.695    0.527
##    .X3                0.431    0.059    7.345    0.000    0.431    0.385
##    .X4                0.402    0.057    7.084    0.000    0.402    0.350
##    .X5                0.421    0.058    7.203    0.000    0.421    0.365
##    .X6                0.521    0.067    7.790    0.000    0.521    0.463
##    .h123              3.295    0.385    8.561    0.000    3.295    0.721
##    .X7                1.111    0.134    8.307    0.000    1.111    0.620
##    .X8                0.569    0.080    7.070    0.000    0.569    0.361
##    .X9                0.452    0.070    6.421    0.000    0.452    0.295
##    .X10               0.580    0.081    7.157    0.000    0.580    0.371
##    .X11               1.475    0.175    8.435    0.000    1.475    0.671
##    .X12               0.907    0.108    8.418    0.000    0.907    0.664
##    .f123              2.633    0.304    8.649    0.000    2.633    0.778
##    .X13               0.755    0.121    6.239    0.000    0.755    0.382
##    .X14               1.266    0.162    7.832    0.000    1.266    0.591
##    .X15               1.515    0.218    6.954    0.000    1.515    0.453
##    .X16               0.909    0.103    8.840    0.000    0.909    0.938
##    .X17               2.047    0.229    8.923    0.000    2.047    0.987
##    .X18               2.185    0.248    8.801    0.000    2.185    0.916
##    .i123              0.998    0.112    8.942    0.000    0.998    0.998
##    .X19               1.595    0.178    8.934    0.000    1.595    0.996
##    .X20               1.438    0.161    8.916    0.000    1.438    0.988
##    .X21               2.259    0.253    8.943    0.000    2.259    0.999
##    .X22               1.206    0.154    7.816    0.000    1.206    0.674
##    .X23               1.002    0.155    6.447    0.000    1.002    0.498
##    .X24               1.148    0.157    7.330    0.000    1.148    0.596
##    .a123              2.852    0.324    8.791    0.000    2.852    0.936
##    .X25               1.034    0.123    8.437    0.000    1.034    0.729
##    .X26               1.513    0.183    8.276    0.000    1.513    0.673
##    .X27               1.314    0.153    8.611    0.000    1.314    0.802
##    .X28               1.616    0.189    8.558    0.000    1.616    0.778
##    .X29               1.088    0.139    7.810    0.000    1.088    0.555
##    .X30               1.282    0.175    7.339    0.000    1.282    0.475
##    .p123              1.921    0.218    8.801    0.000    1.921    0.903
##     harmL             1.000                               1.000    1.000
##     fairL             1.000                               1.000    1.000
##     ingroupL          1.000                               1.000    1.000
##     authorityL        1.000                               1.000    1.000
##     purityL           1.000                               1.000    1.000
## 
## R-Square:
##                    Estimate
##     X1                0.540
##     X2                0.473
##     X3                0.615
##     X4                0.650
##     X5                0.635
##     X6                0.537
##     h123              0.279
##     X7                0.380
##     X8                0.639
##     X9                0.705
##     X10               0.629
##     X11               0.329
##     X12               0.336
##     f123              0.222
##     X13               0.618
##     X14               0.409
##     X15               0.547
##     X16               0.062
##     X17               0.013
##     X18               0.084
##     i123              0.002
##     X19               0.004
##     X20               0.012
##     X21               0.001
##     X22               0.326
##     X23               0.502
##     X24               0.404
##     a123              0.064
##     X25               0.271
##     X26               0.327
##     X27               0.198
##     X28               0.222
##     X29               0.445
##     X30               0.525
##     p123              0.097
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{fitMeasures}\NormalTok{(model6.}\FloatTok{1.}\NormalTok{fit)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##                npar                fmin               chisq 
##              80.000               3.763            1204.242 
##                  df              pvalue      baseline.chisq 
##             550.000               0.000            2813.016 
##         baseline.df     baseline.pvalue                 cfi 
##             595.000               0.000               0.705 
##                 tli                nnfi                 rfi 
##               0.681               0.681               0.537 
##                 nfi                pnfi                 ifi 
##               0.572               0.529               0.711 
##                 rni                logl   unrestricted.logl 
##               0.705           -8769.481           -8167.360 
##                 aic                 bic              ntotal 
##           17698.962           17944.976             160.000 
##                bic2               rmsea      rmsea.ci.lower 
##           17691.725               0.086               0.080 
##      rmsea.ci.upper        rmsea.pvalue                 rmr 
##               0.093               0.000               0.216 
##          rmr_nomean                srmr        srmr_bentler 
##               0.216               0.112               0.112 
## srmr_bentler_nomean         srmr_bollen  srmr_bollen_nomean 
##               0.112               0.112               0.112 
##          srmr_mplus   srmr_mplus_nomean               cn_05 
##               0.112               0.112              81.471 
##               cn_01                 gfi                agfi 
##              84.715               0.696               0.652 
##                pgfi                 mfi                ecvi 
##               0.608               0.129               8.527
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{##perfectly correlated traits}
\NormalTok{model6.}\DecValTok{2}\NormalTok{ =}\StringTok{ '}
\StringTok{harmL =~ X1+X2+X3+X4+X5+X6+h123}
\StringTok{fairL =~ X7+X8+X9+X10+X11+X12+f123}
\StringTok{ingroupL =~ X13+X14+X15+X16+X17+X18+i123}
\StringTok{authorityL =~ X19+X20+X21+X22+X23+X24+a123}
\StringTok{purityL=~ X25+X26+X27+X28+X29+X30+p123}
\StringTok{mfq =~ X1+X2+X3+X4+X5+X6+X7+X8+X9+X10+X11+X12+X13+X14+X15+X16+X17+X18+X19+X20+X21+X22+X23+X24+X25+X26+X27+X28+X29+X30}
\StringTok{mfd =~ h123+f123+i123+a123+p123}

\StringTok{##fix the covariances}
\StringTok{harmL~~0*mfq}
\StringTok{fairL~~0*mfq}
\StringTok{ingroupL~~0*mfq}
\StringTok{authorityL~~0*mfq}
\StringTok{purityL~~0*mfq}
\StringTok{harmL~~0*mfd}
\StringTok{fairL~~0*mfd}
\StringTok{ingroupL~~0*mfd}
\StringTok{authorityL~~0*mfd}
\StringTok{purityL~~0*mfd}

\StringTok{harmL~~1*fairL}
\StringTok{harmL~~1*authorityL}
\StringTok{harmL~~1*purityL}
\StringTok{harmL~~1*ingroupL}
\StringTok{fairL~~1*authorityL}
\StringTok{fairL~~1*purityL}
\StringTok{fairL~~1*ingroupL}
\StringTok{authorityL~~1*purityL}
\StringTok{authorityL~~1*ingroupL}
\StringTok{purityL~~1*ingroupL}
\StringTok{'}

\NormalTok{model6.}\FloatTok{2.}\NormalTok{fit =}\StringTok{ }\KeywordTok{cfa}\NormalTok{(model6.}\DecValTok{2}\NormalTok{, }\DataTypeTok{data=}\NormalTok{mtmmdata, }\DataTypeTok{std.lv=}\OtherTok{TRUE}\NormalTok{)}
\KeywordTok{summary}\NormalTok{(model6.}\FloatTok{2.}\NormalTok{fit, }\DataTypeTok{rsquare=}\OtherTok{TRUE}\NormalTok{, }\DataTypeTok{standardized=}\OtherTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## lavaan (0.5-23.1097) converged normally after  63 iterations
## 
##   Number of observations                           160
## 
##   Estimator                                         ML
##   Minimum Function Test Statistic             1137.944
##   Degrees of freedom                               524
##   P-value (Chi-square)                           0.000
## 
## Parameter Estimates:
## 
##   Information                                 Expected
##   Standard Errors                             Standard
## 
## Latent Variables:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   harmL =~                                                              
##     X1                0.349    0.120    2.915    0.004    0.349    0.336
##     X2                0.280    0.132    2.117    0.034    0.280    0.244
##     X3                0.340    0.130    2.610    0.009    0.340    0.322
##     X4                0.484    0.122    3.975    0.000    0.484    0.452
##     X5                0.360    0.128    2.803    0.005    0.360    0.335
##     X6                0.519    0.114    4.563    0.000    0.519    0.489
##     h123              1.213    0.180    6.730    0.000    1.213    0.567
##   fairL =~                                                              
##     X7               -0.606    0.127   -4.786    0.000   -0.606   -0.453
##     X8               -0.410    0.145   -2.821    0.005   -0.410   -0.326
##     X9               -0.488    0.138   -3.537    0.000   -0.488   -0.395
##     X10              -0.679    0.128   -5.316    0.000   -0.679   -0.543
##     X11              -0.823    0.122   -6.731    0.000   -0.823   -0.555
##     X12              -0.243    0.126   -1.932    0.053   -0.243   -0.208
##     f123             -0.510    0.159   -3.217    0.001   -0.510   -0.277
##   ingroupL =~                                                           
##     X13              -0.760    0.132   -5.749    0.000   -0.760   -0.540
##     X14              -0.575    0.139   -4.144    0.000   -0.575   -0.393
##     X15              -1.191    0.144   -8.248    0.000   -1.191   -0.651
##     X16               0.089    0.104    0.859    0.390    0.089    0.091
##     X17               0.226    0.119    1.896    0.058    0.226    0.157
##     X18              -0.355    0.132   -2.686    0.007   -0.355   -0.230
##     i123             -0.038    0.083   -0.460    0.646   -0.038   -0.038
##   authorityL =~                                                         
##     X19               0.145    0.118    1.228    0.219    0.145    0.115
##     X20               0.007    0.110    0.061    0.951    0.007    0.006
##     X21              -0.067    0.125   -0.540    0.589   -0.067   -0.045
##     X22              -0.594    0.105   -5.675    0.000   -0.594   -0.444
##     X23              -0.746    0.111   -6.719    0.000   -0.746   -0.526
##     X24              -0.697    0.107   -6.520    0.000   -0.697   -0.502
##     a123             -0.244    0.147   -1.657    0.097   -0.244   -0.140
##   purityL =~                                                            
##     X25              -0.454    0.101   -4.518    0.000   -0.454   -0.381
##     X26              -0.791    0.115   -6.904    0.000   -0.791   -0.528
##     X27              -0.478    0.102   -4.670    0.000   -0.478   -0.374
##     X28              -0.579    0.120   -4.808    0.000   -0.579   -0.401
##     X29              -0.845    0.105   -8.038    0.000   -0.845   -0.603
##     X30              -0.982    0.129   -7.586    0.000   -0.982   -0.598
##     p123              0.426    0.119    3.595    0.000    0.426    0.292
##   mfq =~                                                                
##     X1                0.678    0.083    8.176    0.000    0.678    0.653
##     X2                0.740    0.088    8.386    0.000    0.740    0.644
##     X3                0.780    0.081    9.612    0.000    0.780    0.737
##     X4                0.698    0.092    7.621    0.000    0.698    0.652
##     X5                0.752    0.084    8.922    0.000    0.752    0.700
##     X6                0.622    0.095    6.580    0.000    0.622    0.586
##     X7                0.565    0.121    4.667    0.000    0.565    0.422
##     X8                0.825    0.100    8.274    0.000    0.825    0.657
##     X9                0.767    0.103    7.438    0.000    0.767    0.621
##     X10               0.674    0.116    5.788    0.000    0.674    0.539
##     X11               0.383    0.145    2.633    0.008    0.383    0.258
##     X12               0.646    0.092    7.055    0.000    0.646    0.552
##     X13               0.613    0.133    4.593    0.000    0.613    0.436
##     X14               0.603    0.129    4.687    0.000    0.603    0.412
##     X15               0.440    0.190    2.314    0.021    0.440    0.240
##     X16               0.512    0.076    6.774    0.000    0.512    0.520
##     X17               0.095    0.121    0.791    0.429    0.095    0.066
##     X18               0.318    0.131    2.430    0.015    0.318    0.206
##     X19               0.437    0.102    4.288    0.000    0.437    0.345
##     X20               0.373    0.097    3.845    0.000    0.373    0.309
##     X21               0.101    0.124    0.814    0.416    0.101    0.067
##     X22               0.001    0.125    0.005    0.996    0.001    0.000
##     X23               0.189    0.138    1.369    0.171    0.189    0.133
##     X24               0.026    0.134    0.191    0.849    0.026    0.018
##     X25               0.267    0.107    2.500    0.012    0.267    0.224
##     X26              -0.037    0.147   -0.255    0.799   -0.037   -0.025
##     X27              -0.087    0.116   -0.750    0.453   -0.087   -0.068
##     X28               0.304    0.131    2.321    0.020    0.304    0.211
##     X29               0.117    0.143    0.820    0.412    0.117    0.084
##     X30               0.333    0.166    2.007    0.045    0.333    0.203
##   mfd =~                                                                
##     h123              1.697    0.329    5.157    0.000    1.697    0.793
##     f123              1.045    0.221    4.721    0.000    1.045    0.568
##     i123             -0.108    0.084   -1.282    0.200   -0.108   -0.108
##     a123              0.506    0.160    3.167    0.002    0.506    0.290
##     p123             -0.170    0.123   -1.379    0.168   -0.170   -0.117
## 
## Covariances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   harmL ~~                                                              
##     mfq               0.000                               0.000    0.000
##   fairL ~~                                                              
##     mfq               0.000                               0.000    0.000
##   ingroupL ~~                                                           
##     mfq               0.000                               0.000    0.000
##   authorityL ~~                                                         
##     mfq               0.000                               0.000    0.000
##   purityL ~~                                                            
##     mfq               0.000                               0.000    0.000
##   harmL ~~                                                              
##     mfd               0.000                               0.000    0.000
##   fairL ~~                                                              
##     mfd               0.000                               0.000    0.000
##   ingroupL ~~                                                           
##     mfd               0.000                               0.000    0.000
##   authorityL ~~                                                         
##     mfd               0.000                               0.000    0.000
##   purityL ~~                                                            
##     mfd               0.000                               0.000    0.000
##   harmL ~~                                                              
##     fairL             1.000                               1.000    1.000
##     authorityL        1.000                               1.000    1.000
##     purityL           1.000                               1.000    1.000
##     ingroupL          1.000                               1.000    1.000
##   fairL ~~                                                              
##     authorityL        1.000                               1.000    1.000
##     purityL           1.000                               1.000    1.000
##     ingroupL          1.000                               1.000    1.000
##   authorityL ~~                                                         
##     purityL           1.000                               1.000    1.000
##   ingroupL ~~                                                           
##     authorityL        1.000                               1.000    1.000
##     purityL           1.000                               1.000    1.000
##   mfq ~~                                                                
##     mfd               0.355    0.091    3.907    0.000    0.355    0.355
## 
## Variances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##    .X1                0.496    0.062    8.001    0.000    0.496    0.460
##    .X2                0.693    0.084    8.228    0.000    0.693    0.526
##    .X3                0.395    0.053    7.477    0.000    0.395    0.353
##    .X4                0.426    0.056    7.563    0.000    0.426    0.371
##    .X5                0.458    0.059    7.727    0.000    0.458    0.397
##    .X6                0.468    0.060    7.793    0.000    0.468    0.417
##    .h123              0.221    0.912    0.243    0.808    0.221    0.048
##    .X7                1.104    0.131    8.442    0.000    1.104    0.616
##    .X8                0.729    0.091    8.032    0.000    0.729    0.462
##    .X9                0.702    0.088    8.014    0.000    0.702    0.459
##    .X10               0.647    0.083    7.804    0.000    0.647    0.414
##    .X11               1.375    0.163    8.447    0.000    1.375    0.626
##    .X12               0.891    0.104    8.529    0.000    0.891    0.652
##    .f123              2.032    0.412    4.931    0.000    2.032    0.600
##    .X13               1.024    0.125    8.188    0.000    1.024    0.518
##    .X14               1.448    0.169    8.560    0.000    1.448    0.676
##    .X15               1.735    0.212    8.166    0.000    1.735    0.518
##    .X16               0.699    0.081    8.642    0.000    0.699    0.721
##    .X17               2.015    0.226    8.919    0.000    2.015    0.971
##    .X18               2.158    0.244    8.859    0.000    2.158    0.905
##    .i123              0.987    0.110    8.932    0.000    0.987    0.987
##    .X19               1.389    0.157    8.824    0.000    1.389    0.867
##    .X20               1.317    0.149    8.863    0.000    1.317    0.905
##    .X21               2.246    0.251    8.939    0.000    2.246    0.993
##    .X22               1.436    0.164    8.735    0.000    1.436    0.803
##    .X23               1.421    0.165    8.593    0.000    1.421    0.706
##    .X24               1.439    0.166    8.657    0.000    1.439    0.747
##    .a123              2.730    0.317    8.608    0.000    2.730    0.896
##    .X25               1.141    0.130    8.744    0.000    1.141    0.804
##    .X26               1.621    0.188    8.614    0.000    1.621    0.721
##    .X27               1.401    0.159    8.800    0.000    1.401    0.856
##    .X28               1.650    0.189    8.731    0.000    1.650    0.794
##    .X29               1.234    0.146    8.444    0.000    1.234    0.629
##    .X30               1.624    0.194    8.390    0.000    1.624    0.602
##    .p123              1.916    0.218    8.799    0.000    1.916    0.901
##     harmL             1.000                               1.000    1.000
##     fairL             1.000                               1.000    1.000
##     ingroupL          1.000                               1.000    1.000
##     authorityL        1.000                               1.000    1.000
##     purityL           1.000                               1.000    1.000
##     mfq               1.000                               1.000    1.000
##     mfd               1.000                               1.000    1.000
## 
## R-Square:
##                    Estimate
##     X1                0.540
##     X2                0.474
##     X3                0.647
##     X4                0.629
##     X5                0.603
##     X6                0.583
##     h123              0.952
##     X7                0.384
##     X8                0.538
##     X9                0.541
##     X10               0.586
##     X11               0.374
##     X12               0.348
##     f123              0.400
##     X13               0.482
##     X14               0.324
##     X15               0.482
##     X16               0.279
##     X17               0.029
##     X18               0.095
##     i123              0.013
##     X19               0.133
##     X20               0.095
##     X21               0.007
##     X22               0.197
##     X23               0.294
##     X24               0.253
##     a123              0.104
##     X25               0.196
##     X26               0.279
##     X27               0.144
##     X28               0.206
##     X29               0.371
##     X30               0.398
##     p123              0.099
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{fitMeasures}\NormalTok{(model6.}\FloatTok{2.}\NormalTok{fit)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##                npar                fmin               chisq 
##             106.000               3.556            1137.944 
##                  df              pvalue      baseline.chisq 
##             524.000               0.000            2813.016 
##         baseline.df     baseline.pvalue                 cfi 
##             595.000               0.000               0.723 
##                 tli                nnfi                 rfi 
##               0.686               0.686               0.541 
##                 nfi                pnfi                 ifi 
##               0.595               0.524               0.732 
##                 rni                logl   unrestricted.logl 
##               0.723           -8736.332           -8167.360 
##                 aic                 bic              ntotal 
##           17684.664           18010.632             160.000 
##                bic2               rmsea      rmsea.ci.lower 
##           17675.075               0.086               0.079 
##      rmsea.ci.upper        rmsea.pvalue                 rmr 
##               0.092               0.000               0.155 
##          rmr_nomean                srmr        srmr_bentler 
##               0.155               0.079               0.079 
## srmr_bentler_nomean         srmr_bollen  srmr_bollen_nomean 
##               0.079               0.079               0.079 
##          srmr_mplus   srmr_mplus_nomean               cn_05 
##               0.079               0.079              82.320 
##               cn_01                 gfi                agfi 
##              85.677               0.671               0.604 
##                pgfi                 mfi                ecvi 
##               0.558               0.147               8.437
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{##no method correl}
\NormalTok{model6.}\DecValTok{3}\NormalTok{ =}\StringTok{ '}
\StringTok{harmL =~ X1+X2+X3+X4+X5+X6+h123}
\StringTok{fairL =~ X7+X8+X9+X10+X11+X12+f123}
\StringTok{ingroupL =~ X13+X14+X15+X16+X17+X18+i123}
\StringTok{authorityL =~ X19+X20+X21+X22+X23+X24+a123}
\StringTok{purityL=~ X25+X26+X27+X28+X29+X30+p123}
\StringTok{mfq =~ X1+X2+X3+X4+X5+X6+X7+X8+X9+X10+X11+X12+X13+X14+X15+X16+X17+X18+X19+X20+X21+X22+X23+X24+X25+X26+X27+X28+X29+X30}
\StringTok{mfd =~ h123+f123+i123+a123+p123}

\StringTok{##fix the covariances}
\StringTok{harmL~~0*mfq}
\StringTok{fairL~~0*mfq}
\StringTok{ingroupL~~0*mfq}
\StringTok{authorityL~~0*mfq}
\StringTok{purityL~~0*mfq}
\StringTok{harmL~~0*mfd}
\StringTok{fairL~~0*mfd}
\StringTok{ingroupL~~0*mfd}
\StringTok{authorityL~~0*mfd}
\StringTok{purityL~~0*mfd}
\StringTok{authorityL~~.80*purityL}
\StringTok{mfq~~0*mfd}
\StringTok{'}

\NormalTok{model6.}\FloatTok{3.}\NormalTok{fit =}\StringTok{ }\KeywordTok{cfa}\NormalTok{(model6.}\DecValTok{3}\NormalTok{, }\DataTypeTok{data=}\NormalTok{mtmmdata, }\DataTypeTok{std.lv=}\OtherTok{TRUE}\NormalTok{)}
\KeywordTok{summary}\NormalTok{(model6.}\FloatTok{3.}\NormalTok{fit, }\DataTypeTok{rsquare=}\OtherTok{TRUE}\NormalTok{, }\DataTypeTok{standardized=}\OtherTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## lavaan (0.5-23.1097) converged normally after  44 iterations
## 
##   Number of observations                           160
## 
##   Estimator                                         ML
##   Minimum Function Test Statistic              904.250
##   Degrees of freedom                               516
##   P-value (Chi-square)                           0.000
## 
## Parameter Estimates:
## 
##   Information                                 Expected
##   Standard Errors                             Standard
## 
## Latent Variables:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   harmL =~                                                              
##     X1                0.423    0.078    5.450    0.000    0.423    0.419
##     X2                0.350    0.088    3.992    0.000    0.350    0.312
##     X3                0.415    0.075    5.505    0.000    0.415    0.405
##     X4                0.654    0.077    8.536    0.000    0.654    0.631
##     X5                0.575    0.078    7.359    0.000    0.575    0.553
##     X6                0.708    0.077    9.196    0.000    0.708    0.686
##     h123              1.259    0.143    8.782    0.000    1.259    0.604
##   fairL =~                                                              
##     X7                0.745    0.103    7.232    0.000    0.745    0.552
##     X8                0.823    0.087    9.431    0.000    0.823    0.644
##     X9                0.889    0.084   10.548    0.000    0.889    0.707
##     X10               0.884    0.088   10.098    0.000    0.884    0.697
##     X11               0.966    0.114    8.513    0.000    0.966    0.650
##     X12               0.488    0.090    5.410    0.000    0.488    0.413
##     f123              1.291    0.131    9.847    0.000    1.291    0.648
##   ingroupL =~                                                           
##     X13               0.946    0.103    9.136    0.000    0.946    0.660
##     X14               0.793    0.115    6.913    0.000    0.793    0.536
##     X15               1.395    0.135   10.307    0.000    1.395    0.754
##     X16              -0.012    0.079   -0.148    0.882   -0.012   -0.012
##     X17              -0.331    0.123   -2.695    0.007   -0.331   -0.231
##     X18               0.268    0.130    2.056    0.040    0.268    0.173
##     i123              0.029    0.087    0.337    0.736    0.029    0.029
##   authorityL =~                                                         
##     X19               0.015    0.107    0.142    0.887    0.015    0.012
##     X20               0.072    0.103    0.704    0.481    0.072    0.060
##     X21               0.065    0.133    0.487    0.626    0.065    0.043
##     X22               0.746    0.108    6.879    0.000    0.746    0.558
##     X23               0.964    0.111    8.722    0.000    0.964    0.677
##     X24               0.871    0.110    7.911    0.000    0.871    0.629
##     a123              0.590    0.145    4.077    0.000    0.590    0.332
##   purityL =~                                                            
##     X25               0.563    0.095    5.950    0.000    0.563    0.471
##     X26               0.894    0.116    7.738    0.000    0.894    0.600
##     X27               0.599    0.103    5.810    0.000    0.599    0.470
##     X28               0.616    0.116    5.292    0.000    0.616    0.426
##     X29               0.941    0.104    9.018    0.000    0.941    0.674
##     X30               1.134    0.120    9.470    0.000    1.134    0.689
##     p123             -0.450    0.122   -3.678    0.000   -0.450   -0.308
##   mfq =~                                                                
##     X1                0.606    0.075    8.033    0.000    0.606    0.600
##     X2                0.731    0.084    8.690    0.000    0.731    0.650
##     X3                0.736    0.072   10.157    0.000    0.736    0.718
##     X4                0.479    0.077    6.243    0.000    0.479    0.462
##     X5                0.538    0.077    6.950    0.000    0.538    0.517
##     X6                0.363    0.078    4.661    0.000    0.363    0.352
##     X7                0.417    0.106    3.945    0.000    0.417    0.308
##     X8                0.614    0.091    6.738    0.000    0.614    0.481
##     X9                0.561    0.088    6.355    0.000    0.561    0.446
##     X10               0.501    0.091    5.488    0.000    0.501    0.395
##     X11               0.172    0.116    1.477    0.140    0.172    0.115
##     X12               0.538    0.092    5.823    0.000    0.538    0.455
##     X13               0.621    0.112    5.536    0.000    0.621    0.434
##     X14               0.516    0.121    4.268    0.000    0.516    0.348
##     X15               0.392    0.150    2.624    0.009    0.392    0.212
##     X16               0.596    0.078    7.676    0.000    0.596    0.605
##     X17               0.276    0.124    2.232    0.026    0.276    0.192
##     X18               0.545    0.130    4.182    0.000    0.545    0.351
##     X19               0.571    0.104    5.481    0.000    0.571    0.451
##     X20               0.488    0.101    4.857    0.000    0.488    0.404
##     X21               0.152    0.131    1.162    0.245    0.152    0.101
##     X22               0.167    0.111    1.503    0.133    0.167    0.125
##     X23               0.358    0.115    3.124    0.002    0.358    0.251
##     X24               0.159    0.114    1.391    0.164    0.159    0.115
##     X25               0.312    0.100    3.125    0.002    0.312    0.261
##     X26              -0.022    0.125   -0.179    0.858   -0.022   -0.015
##     X27              -0.043    0.109   -0.399    0.690   -0.043   -0.034
##     X28               0.325    0.122    2.665    0.008    0.325    0.225
##     X29               0.141    0.116    1.219    0.223    0.141    0.101
##     X30               0.427    0.134    3.194    0.001    0.427    0.260
##   mfd =~                                                                
##     h123              1.389    0.173    8.014    0.000    1.389    0.666
##     f123              1.188    0.154    7.735    0.000    1.188    0.597
##     i123             -0.102    0.092   -1.104    0.270   -0.102   -0.102
##     a123              0.795    0.150    5.280    0.000    0.795    0.446
##     p123             -0.049    0.129   -0.383    0.702   -0.049   -0.034
## 
## Covariances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   harmL ~~                                                              
##     mfq               0.000                               0.000    0.000
##   fairL ~~                                                              
##     mfq               0.000                               0.000    0.000
##   ingroupL ~~                                                           
##     mfq               0.000                               0.000    0.000
##   authorityL ~~                                                         
##     mfq               0.000                               0.000    0.000
##   purityL ~~                                                            
##     mfq               0.000                               0.000    0.000
##   harmL ~~                                                              
##     mfd               0.000                               0.000    0.000
##   fairL ~~                                                              
##     mfd               0.000                               0.000    0.000
##   ingroupL ~~                                                           
##     mfd               0.000                               0.000    0.000
##   authorityL ~~                                                         
##     mfd               0.000                               0.000    0.000
##   purityL ~~                                                            
##     mfd               0.000                               0.000    0.000
##   authorityL ~~                                                         
##     purityL           0.800                               0.800    0.800
##   mfq ~~                                                                
##     mfd               0.000                               0.000    0.000
##   harmL ~~                                                              
##     fairL            -0.085    0.108   -0.789    0.430   -0.085   -0.085
##     ingroupL         -0.409    0.106   -3.859    0.000   -0.409   -0.409
##     authorityL       -0.633    0.094   -6.735    0.000   -0.633   -0.633
##     purityL          -0.511    0.093   -5.480    0.000   -0.511   -0.511
##   fairL ~~                                                              
##     ingroupL          0.619    0.071    8.677    0.000    0.619    0.619
##     authorityL        0.300    0.098    3.050    0.002    0.300    0.300
##     purityL           0.412    0.088    4.665    0.000    0.412    0.412
##   ingroupL ~~                                                           
##     authorityL        0.404    0.088    4.604    0.000    0.404    0.404
##     purityL           0.800    0.059   13.592    0.000    0.800    0.800
## 
## Variances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##    .X1                0.474    0.060    7.924    0.000    0.474    0.465
##    .X2                0.606    0.078    7.814    0.000    0.606    0.480
##    .X3                0.337    0.049    6.907    0.000    0.337    0.321
##    .X4                0.417    0.057    7.254    0.000    0.417    0.388
##    .X5                0.462    0.060    7.701    0.000    0.462    0.427
##    .X6                0.431    0.062    6.904    0.000    0.431    0.405
##    .h123              0.836    0.385    2.172    0.030    0.836    0.192
##    .X7                1.096    0.132    8.321    0.000    1.096    0.600
##    .X8                0.578    0.078    7.440    0.000    0.578    0.354
##    .X9                0.478    0.069    6.886    0.000    0.478    0.302
##    .X10               0.577    0.080    7.262    0.000    0.577    0.359
##    .X11               1.250    0.161    7.757    0.000    1.250    0.565
##    .X12               0.869    0.103    8.465    0.000    0.869    0.622
##    .f123              0.883    0.287    3.072    0.002    0.883    0.223
##    .X13               0.772    0.116    6.646    0.000    0.772    0.376
##    .X14               1.299    0.162    8.017    0.000    1.299    0.592
##    .X15               1.318    0.214    6.152    0.000    1.318    0.386
##    .X16               0.614    0.079    7.763    0.000    0.614    0.634
##    .X17               1.877    0.216    8.680    0.000    1.877    0.910
##    .X18               2.035    0.234    8.692    0.000    2.035    0.847
##    .i123              0.987    0.111    8.907    0.000    0.987    0.989
##    .X19               1.276    0.151    8.454    0.000    1.276    0.796
##    .X20               1.217    0.142    8.565    0.000    1.217    0.833
##    .X21               2.235    0.251    8.921    0.000    2.235    0.988
##    .X22               1.203    0.153    7.860    0.000    1.203    0.673
##    .X23               0.971    0.148    6.541    0.000    0.971    0.479
##    .X24               1.134    0.154    7.367    0.000    1.134    0.591
##    .a123              2.187    0.287    7.624    0.000    2.187    0.691
##    .X25               1.013    0.120    8.434    0.000    1.013    0.710
##    .X26               1.421    0.178    7.961    0.000    1.421    0.640
##    .X27               1.263    0.150    8.435    0.000    1.263    0.778
##    .X28               1.602    0.187    8.565    0.000    1.602    0.768
##    .X29               1.043    0.137    7.589    0.000    1.043    0.535
##    .X30               1.240    0.170    7.304    0.000    1.240    0.458
##    .p123              1.923    0.219    8.773    0.000    1.923    0.904
##     harmL             1.000                               1.000    1.000
##     fairL             1.000                               1.000    1.000
##     ingroupL          1.000                               1.000    1.000
##     authorityL        1.000                               1.000    1.000
##     purityL           1.000                               1.000    1.000
##     mfq               1.000                               1.000    1.000
##     mfd               1.000                               1.000    1.000
## 
## R-Square:
##                    Estimate
##     X1                0.535
##     X2                0.520
##     X3                0.679
##     X4                0.612
##     X5                0.573
##     X6                0.595
##     h123              0.808
##     X7                0.400
##     X8                0.646
##     X9                0.698
##     X10               0.641
##     X11               0.435
##     X12               0.378
##     f123              0.777
##     X13               0.624
##     X14               0.408
##     X15               0.614
##     X16               0.366
##     X17               0.090
##     X18               0.153
##     i123              0.011
##     X19               0.204
##     X20               0.167
##     X21               0.012
##     X22               0.327
##     X23               0.521
##     X24               0.409
##     a123              0.309
##     X25               0.290
##     X26               0.360
##     X27               0.222
##     X28               0.232
##     X29               0.465
##     X30               0.542
##     p123              0.096
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{fitMeasures}\NormalTok{(model6.}\FloatTok{3.}\NormalTok{fit)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##                npar                fmin               chisq 
##             114.000               2.826             904.250 
##                  df              pvalue      baseline.chisq 
##             516.000               0.000            2813.016 
##         baseline.df     baseline.pvalue                 cfi 
##             595.000               0.000               0.825 
##                 tli                nnfi                 rfi 
##               0.798               0.798               0.629 
##                 nfi                pnfi                 ifi 
##               0.679               0.588               0.831 
##                 rni                logl   unrestricted.logl 
##               0.825           -8619.485           -8167.360 
##                 aic                 bic              ntotal 
##           17466.970           17817.540             160.000 
##                bic2               rmsea      rmsea.ci.lower 
##           17456.658               0.069               0.061 
##      rmsea.ci.upper        rmsea.pvalue                 rmr 
##               0.076               0.000               0.161 
##          rmr_nomean                srmr        srmr_bentler 
##               0.161               0.080               0.080 
## srmr_bentler_nomean         srmr_bollen  srmr_bollen_nomean 
##               0.080               0.077               0.077 
##          srmr_mplus   srmr_mplus_nomean               cn_05 
##               0.078               0.078             101.849 
##               cn_01                 gfi                agfi 
##             106.044               0.754               0.700 
##                pgfi                 mfi                ecvi 
##               0.618               0.297               7.077
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{####fix the model####}
\NormalTok{model6.}\DecValTok{4}\NormalTok{ =}\StringTok{ '}
\StringTok{harmL =~ X1+X2+X4+X5+X6+h123}
\StringTok{fairL =~ X7+X8+X9+X10+X11+X12+f123}
\StringTok{ingroupL =~ X13+X14+X15+X17}
\StringTok{authorityL =~ X22+X23+X24+a123}
\StringTok{purityL=~ X25+X26+X27+X29+X30+p123}
\StringTok{mfq =~ X1+X2+X4+X5+X6+X7+X8+X9+X10+X11+X12+X13+X14+X15+X17+X22+X23+X24+X25+X26+X27+X29+X30}
\StringTok{mfd =~ h123+f123+a123+p123}

\StringTok{##fix the covariances}
\StringTok{harmL~~0*mfq}
\StringTok{fairL~~0*mfq}
\StringTok{ingroupL~~0*mfq}
\StringTok{authorityL~~0*mfq}
\StringTok{purityL~~0*mfq}
\StringTok{harmL~~0*mfd}
\StringTok{fairL~~0*mfd}
\StringTok{ingroupL~~0*mfd}
\StringTok{authorityL~~0*mfd}
\StringTok{purityL~~0*mfd}
\StringTok{authorityL~~.60*purityL}
\StringTok{h123~~2.44*h123}
\StringTok{f123~~1.85*f123}
\StringTok{'}

\NormalTok{model6.}\FloatTok{4.}\NormalTok{fit =}\StringTok{ }\KeywordTok{cfa}\NormalTok{(model6.}\DecValTok{4}\NormalTok{, }\DataTypeTok{data=}\NormalTok{mtmmdata, }\DataTypeTok{std.lv=}\OtherTok{TRUE}\NormalTok{)}
\KeywordTok{summary}\NormalTok{(model6.}\FloatTok{4.}\NormalTok{fit, }\DataTypeTok{rsquare=}\OtherTok{TRUE}\NormalTok{, }\DataTypeTok{standardized=}\OtherTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## lavaan (0.5-23.1097) converged normally after  59 iterations
## 
##   Number of observations                           160
## 
##   Estimator                                         ML
##   Minimum Function Test Statistic              516.820
##   Degrees of freedom                               289
##   P-value (Chi-square)                           0.000
## 
## Parameter Estimates:
## 
##   Information                                 Expected
##   Standard Errors                             Standard
## 
## Latent Variables:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   harmL =~                                                              
##     X1                0.673    0.076    8.807    0.000    0.673    0.647
##     X2                0.771    0.084    9.193    0.000    0.771    0.663
##     X4                0.923    0.069   13.448    0.000    0.923    0.871
##     X5                0.919    0.071   12.996    0.000    0.919    0.854
##     X6                0.727    0.074    9.815    0.000    0.727    0.696
##     h123              1.167    0.167    7.007    0.000    1.167    0.507
##   fairL =~                                                              
##     X7                0.658    0.100    6.596    0.000    0.658    0.499
##     X8                0.972    0.085   11.443    0.000    0.972    0.785
##     X9                1.036    0.081   12.842    0.000    1.036    0.850
##     X10               0.778    0.084    9.270    0.000    0.778    0.638
##     X11               0.639    0.113    5.680    0.000    0.639    0.437
##     X12               0.604    0.090    6.698    0.000    0.604    0.521
##     f123              1.057    0.145    7.288    0.000    1.057    0.536
##   ingroupL =~                                                           
##     X13               0.638    0.119    5.380    0.000    0.638    0.455
##     X14               0.908    0.137    6.621    0.000    0.908    0.622
##     X15               0.401    0.157    2.549    0.011    0.401    0.219
##     X17              -0.079    0.141   -0.557    0.577   -0.079   -0.055
##   authorityL =~                                                         
##     X22               0.431    0.121    3.548    0.000    0.431    0.328
##     X23               0.830    0.132    6.269    0.000    0.830    0.605
##     X24               0.562    0.125    4.481    0.000    0.562    0.414
##     a123              0.649    0.168    3.857    0.000    0.649    0.369
##   purityL =~                                                            
##     X25               0.154    0.116    1.332    0.183    0.154    0.130
##     X26               0.560    0.143    3.915    0.000    0.560    0.381
##     X27               0.828    0.147    5.616    0.000    0.828    0.662
##     X29               0.325    0.132    2.464    0.014    0.325    0.236
##     X30               0.126    0.156    0.808    0.419    0.126    0.077
##     p123             -0.259    0.148   -1.747    0.081   -0.259   -0.178
##   mfq =~                                                                
##     X1                0.043    0.090    0.477    0.633    0.043    0.041
##     X2                0.211    0.100    2.118    0.034    0.211    0.181
##     X4               -0.101    0.091   -1.107    0.268   -0.101   -0.095
##     X5                0.037    0.093    0.404    0.686    0.037    0.035
##     X6               -0.190    0.089   -2.136    0.033   -0.190   -0.182
##     X7                0.461    0.111    4.167    0.000    0.461    0.349
##     X8                0.267    0.107    2.509    0.012    0.267    0.216
##     X9                0.252    0.105    2.396    0.017    0.252    0.207
##     X10               0.554    0.100    5.554    0.000    0.554    0.455
##     X11               0.527    0.122    4.308    0.000    0.527    0.360
##     X12               0.214    0.100    2.142    0.032    0.214    0.184
##     X13               0.901    0.112    8.048    0.000    0.901    0.643
##     X14               0.625    0.128    4.879    0.000    0.625    0.428
##     X15               1.321    0.138    9.592    0.000    1.321    0.723
##     X17              -0.168    0.125   -1.351    0.177   -0.168   -0.117
##     X22               0.591    0.108    5.491    0.000    0.591    0.451
##     X23               0.563    0.115    4.889    0.000    0.563    0.411
##     X24               0.570    0.112    5.065    0.000    0.570    0.420
##     X25               0.642    0.095    6.776    0.000    0.642    0.543
##     X26               0.690    0.125    5.537    0.000    0.690    0.469
##     X27               0.340    0.119    2.864    0.004    0.340    0.272
##     X29               0.829    0.109    7.569    0.000    0.829    0.600
##     X30               1.228    0.120   10.189    0.000    1.228    0.752
##   mfd =~                                                                
##     h123              1.221    0.178    6.877    0.000    1.221    0.531
##     f123              0.962    0.157    6.141    0.000    0.962    0.488
##     a123              0.689    0.177    3.883    0.000    0.689    0.392
##     p123              0.107    0.152    0.704    0.481    0.107    0.073
## 
## Covariances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   harmL ~~                                                              
##     mfq               0.000                               0.000    0.000
##   fairL ~~                                                              
##     mfq               0.000                               0.000    0.000
##   ingroupL ~~                                                           
##     mfq               0.000                               0.000    0.000
##   authorityL ~~                                                         
##     mfq               0.000                               0.000    0.000
##   purityL ~~                                                            
##     mfq               0.000                               0.000    0.000
##   harmL ~~                                                              
##     mfd               0.000                               0.000    0.000
##   fairL ~~                                                              
##     mfd               0.000                               0.000    0.000
##   ingroupL ~~                                                           
##     mfd               0.000                               0.000    0.000
##   authorityL ~~                                                         
##     mfd               0.000                               0.000    0.000
##   purityL ~~                                                            
##     mfd               0.000                               0.000    0.000
##   authorityL ~~                                                         
##     purityL           0.600                               0.600    0.600
##   harmL ~~                                                              
##     fairL             0.399    0.078    5.110    0.000    0.399    0.399
##     ingroupL          0.325    0.114    2.856    0.004    0.325    0.325
##     authorityL       -0.203    0.111   -1.819    0.069   -0.203   -0.203
##     purityL          -0.286    0.115   -2.486    0.013   -0.286   -0.286
##   fairL ~~                                                              
##     ingroupL          0.587    0.097    6.074    0.000    0.587    0.587
##     authorityL        0.194    0.114    1.699    0.089    0.194    0.194
##     purityL          -0.040    0.122   -0.326    0.745   -0.040   -0.040
##   ingroupL ~~                                                           
##     authorityL       -0.275    0.164   -1.683    0.092   -0.275   -0.275
##     purityL          -0.388    0.186   -2.084    0.037   -0.388   -0.388
##   mfq ~~                                                                
##     mfd              -0.241    0.128   -1.879    0.060   -0.241   -0.241
## 
## Variances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##    .h123              2.440                               2.440    0.461
##    .f123              1.850                               1.850    0.475
##    .X1                0.628    0.076    8.220    0.000    0.628    0.580
##    .X2                0.715    0.090    7.989    0.000    0.715    0.528
##    .X4                0.261    0.047    5.558    0.000    0.261    0.232
##    .X5                0.312    0.051    6.110    0.000    0.312    0.269
##    .X6                0.527    0.067    7.848    0.000    0.527    0.483
##    .X7                1.094    0.130    8.446    0.000    1.094    0.629
##    .X8                0.517    0.078    6.671    0.000    0.517    0.337
##    .X9                0.350    0.067    5.185    0.000    0.350    0.235
##    .X10               0.575    0.076    7.583    0.000    0.575    0.387
##    .X11               1.454    0.170    8.550    0.000    1.454    0.679
##    .X12               0.935    0.110    8.499    0.000    0.935    0.695
##    .X13               0.747    0.121    6.175    0.000    0.747    0.380
##    .X14               0.914    0.187    4.894    0.000    0.914    0.429
##    .X15               1.433    0.203    7.068    0.000    1.433    0.429
##    .X17               2.040    0.229    8.921    0.000    2.040    0.983
##    .X22               1.186    0.148    8.023    0.000    1.186    0.689
##    .X23               0.874    0.175    4.993    0.000    0.874    0.465
##    .X24               1.197    0.159    7.549    0.000    1.197    0.652
##    .a123              2.200    0.326    6.740    0.000    2.200    0.711
##    .X25               0.963    0.116    8.269    0.000    0.963    0.688
##    .X26               1.374    0.183    7.514    0.000    1.374    0.635
##    .X27               0.763    0.199    3.826    0.000    0.763    0.488
##    .X29               1.112    0.142    7.834    0.000    1.112    0.584
##    .X30               1.144    0.171    6.686    0.000    1.144    0.429
##    .p123              2.045    0.235    8.701    0.000    2.045    0.963
##     harmL             1.000                               1.000    1.000
##     fairL             1.000                               1.000    1.000
##     ingroupL          1.000                               1.000    1.000
##     authorityL        1.000                               1.000    1.000
##     purityL           1.000                               1.000    1.000
##     mfq               1.000                               1.000    1.000
##     mfd               1.000                               1.000    1.000
## 
## R-Square:
##                    Estimate
##     h123              0.539
##     f123              0.525
##     X1                0.420
##     X2                0.472
##     X4                0.768
##     X5                0.731
##     X6                0.517
##     X7                0.371
##     X8                0.663
##     X9                0.765
##     X10               0.613
##     X11               0.321
##     X12               0.305
##     X13               0.620
##     X14               0.571
##     X15               0.571
##     X17               0.017
##     X22               0.311
##     X23               0.535
##     X24               0.348
##     a123              0.289
##     X25               0.312
##     X26               0.365
##     X27               0.512
##     X29               0.416
##     X30               0.571
##     p123              0.037
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{fitMeasures}\NormalTok{(model6.}\FloatTok{4.}\NormalTok{fit) }
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##                npar                fmin               chisq 
##              89.000               1.615             516.820 
##                  df              pvalue      baseline.chisq 
##             289.000               0.000            2101.504 
##         baseline.df     baseline.pvalue                 cfi 
##             351.000               0.000               0.870 
##                 tli                nnfi                 rfi 
##               0.842               0.842               0.701 
##                 nfi                pnfi                 ifi 
##               0.754               0.621               0.874 
##                 rni                logl   unrestricted.logl 
##               0.870           -6697.756           -6439.346 
##                 aic                 bic              ntotal 
##           13573.512           13847.202             160.000 
##                bic2               rmsea      rmsea.ci.lower 
##           13565.461               0.070               0.060 
##      rmsea.ci.upper        rmsea.pvalue                 rmr 
##               0.080               0.001               0.205 
##          rmr_nomean                srmr        srmr_bentler 
##               0.205               0.090               0.090 
## srmr_bentler_nomean         srmr_bollen  srmr_bollen_nomean 
##               0.090               0.088               0.088 
##          srmr_mplus   srmr_mplus_nomean               cn_05 
##               0.089               0.089             103.054 
##               cn_01                 gfi                agfi 
##             108.690               0.815               0.759 
##                pgfi                 mfi                ecvi 
##               0.623               0.491               4.343
\end{verbatim}

\subsection{Results}\label{results}

Data Cleaning and Descriptives. In sample 1, participants who wrote less
than 50 words were deleted (\emph{n} = 69) leaving \emph{n} = 221
participants. The average political orientation was 4.80 (\emph{SD} =
2.21) on a scale of 1 (\emph{conservative}) to 10 (\emph{liberal}). In
sample 2, all 160 participants wrote at least 50 words. The mean
political orientation was 5.01 (\emph{SD} = 2.33) for sample 2. The data
from sample 1 and sample 2 were combined. Before any analyses were
conducted, participants who did not use any words from the MFD were
deleted; 16 participants were deleted from sample 1 and 25 from sample
2. The final sample size for analysis was \emph{N} = 340 which had a
mean political orientation of 4.90 (\emph{SD} = 2.28). MFD scores were
computed using NVivo \emph{(CITE)} as both frequency for each foundation
and percent coverage for each foundation. Frequency was simply the count
of the number of words used from a given foundation dictionary; for
example, a participant using the word \emph{war} once and the word
\emph{peace} twice would have a frequency score of 3 for the \emph{harm}
dictionary. Percent coverage was calculated by taking the frequency and
dividing by the word count; for example, given a frequency score of 3
for the \emph{harm} dictionary and a word count of 100, then the percent
coverage would be .03 for the \emph{harm} dictionary. MFQ scores for
each foundation were calculated by averaging the six items pertaining to
each foundation. Reliability. Here we should talk about the reliability
of the MFQ for each piece, as well as the reliability of the words for
the MFD. I think to do that you might need a thing that has each word as
frequency count yes/no or however the LIWC version thing was done. MTMM.
BASIC SEM STUFF HERE (also that you used bayes) Data screening was
conducted using SPSS version 22 and AMOS version 22. Participants who
were missing data for the MFD, MFQ, or political orientation were
deleted from all analyses. Given the distribution of the dictionary
variables, participants whose writing sample were less than 2\% words
from the MFD were deleted resulting in a sample size of 252.
Additionally, 7 outliers were deleted. Widaman's (1985; as cited in
({\textbf{???}})) four-step nested method was used to test the
convergent and divergent validity of the MFD and MFQ. The first step is
the baseline model (Model 1), which establishes correlation among traits
(\emph{harm}, \emph{purity}, \emph{fairness}, \emph{authority}, and
\emph{ingroup}) as well as correlation among methods (MFD and MFQ) but
no cross correlation of traits and methods. The individual questions
from the 30 item version of the MFQ and the total frequency of concepts
from each foundation in the MFD were used as measured variables. The fit
of this first model indicated some misfit, as fit indices were a mix of
poor and acceptable, \(\chi\) 2 (514) = 977.46, \(\chi\) 2/df = 1.90,
CFI = .842, RMSEA = .061 {[}95\% CI = .055-.067{]}, SRMR = .0623. In
this model, the MFD \emph{harm}, \emph{fairness}, and \emph{ingroup}
items significantly loaded onto their trait factors, while
\emph{authority} and \emph{purity} did not. All foundations but
\emph{authority} loaded significantly on the method traits. All but two
of the \emph{ingroup} questions and one \emph{authority} question loaded
onto the MFQ trait factors. Several questions of the MFQ did not load
significantly onto the methods factors; however, this result was taken
as an indicator that traits variance was higher than methods variance.
Generally, trait loadings were higher than method loadings for both the
MFD and MFQ for \emph{harm} and \emph{fairness} traits. However, the
\emph{purity}, \emph{ingroup}, and \emph{authority} foundations did not
show this loading pattern. ERIN STOPPED HERE CUZ HEADACHE. The second
step (Model 2) involved eliminating the latent traits from the model.
This model was significantly worse than Model 1 indicating the traits
are important to the model (\(\delta\) \(\chi\) 2 = 1141.09, \(\delta\)
df = 45, \(\delta\) CFI = .351). This supports convergent validity for
the traits measured by both methods which in this case are the five
moral foundations. The third step (Model 3) involved forcing the five
traits to be perfectly correlated. This model was significantly worse
than Model 1 indicating the usefulness of five unique traits (\(\delta\)
\(\chi\) 2 = 311.09, \(\delta\) df = 10, \(\delta\) CFI = .097). This
supports discriminant validity for the existence of five unique moral
foundations. The final step (Model 4) involved allowing the correlations
between the traits to be freely estimated and forcing the methods to be
uncorrelated. This model was similar to Model 1 indicating the methods
both measure the traits but they are both unique methods (\(\delta\)
\(\chi\) 2 = 2.23, \(\delta\) df = 1, \(\delta\) CFI = .001). This
supports discriminant validity for the methods. This set of analyses
suggests the MFD is a possibly valid measure of moral foundations but
does not measure them well enough to be useful in all applications and
may be measuring them differently than the MFQ.\\
Regression predicting Political Orientation. The MFQ has predicted
political orientation across many studies (Federico et al., 2013; Graham
et al., 2009; Haidt, Graham, \& Joseph, 2009; Weber \& Federico, 2013).
Therefore, in addition to the MTMM analysis, we compared how well the
MFD score predicted political orientation compared to how well the MFQ
predicted the political orientation. First, total MFQ scores were
calculated for each foundation by averaging all six items. Then, a
regression analysis was conducted with the five MFQ foundation score
predicting political orientation. The overall model was significant,
\emph{R2} = .35, \emph{F} (5, 255) = 26.91, \emph{p} \textless{} .05.
Higher scores on the harm and fairness foundations predicted a more
liberal political orientation with harm accounting for 3\% of the
variance and fairness accounting for 6\%. Higher scores on ingroup,
authority, and purity predicted a more conservative orientation
accounting for 1\%, 2\%, and 8\% on the variance respectively. See
\emph{table ?} for regression coefficients. Next, a regression analysis
was conducted to determine how well the five MFD scores predicted
political orientation. The overall model was not significant, \emph{R2}
= .16, \emph{F} (5, 255) = 1.36, \emph{p} = .241. Higher harm scores
somewhat predicted more liberal orientation accounting for 1\% of the
variance in political orientation. Higher purity scores somewhat
predicted more conservative orientation accounting for 1\% of the
variance. See \emph{table ?} for regression coefficients.

\subsection{Study 2}\label{study-2}

In Study 2, the MFD was applied to real-world data, U.S. Congressional
speeches. The purpose of this study was to further test the predictive
validity of the MFD. If valid, the MFD should detect political party
differences in congressional speeches.

\subsection{Method}\label{method-1}

\section{Sample}\label{sample}

Speeches were gathered through the Congressional Record available
through the U.S. Government Publishing Office. Speeches were gathered
from the following venues from 1998-2013: Senate, House of
Representatives, Senate Foreign Affairs Committee, and House Foreign
Affairs Committee. The topics of the speeches were U.S. foreign policy
with the following nations: Iraq, Iran, North Korea, Afghanistan,
Kosovo, Libya, Russia, Sudan, and Syria. These speeches often deal with
the use of military force and the enforcement of sanctions which should
include moral arguments. A total of 5207 Congressional speeches were
gathered. These speeches were made by 509 unique speakers. Republicans
gave 2268 speeches, and Democrats gave 2939 speeches. \# Data Processing
For each speech, the number of words used from each of the five
foundation dictionary was calculated. So, each speech had a word
frequency count for each foundation. Speeches which did not contain any
words from any foundation dictionary were excluded. Across speeches,
there were a total of 2,026,243 words. Of these, 7838 (.39\%) were
\emph{harm} words, 1976 (.10\%) were \emph{fairness} words, 2985 (.15\%)
were \emph{ingroup} words, 4057 (.20\%) were \emph{authority} words, and
717 (.04\%) were \emph{purity} words.

\subsection{Results}\label{results-1}

Bayesian \emph{t}-tests were used to compare the Democratic and
Republican use of MFD words. For \emph{harm} words, the Bayes factor
comparing a model of equal use between Democrats and Republicans and a
model of greater use by Democrats was .08. In other words, equal use of
\emph{harm} words by both parties is more likely. Examining the means
revealed that Democrats (\emph{M} = 5.62, \emph{SD} = 8.12), on average,
used less than one more \emph{harm} word than Republicans (\emph{M} =
4.87, \emph{SD} = 6.32). For \emph{fairness} words, the Bayes factor was
.04; once again, equal use of \emph{fairness} words by both parties is
more likely. Essentially no difference exists between the mean use for
Democrats (\emph{M} = 2.46, \emph{SD} = 2.74) and Republicans (\emph{M}
= 2.66, \emph{SD} = 3.34). For \emph{ingroup}, \emph{authority}, and
\emph{purity} words, a model of equal use was tested against a model of
greater use by Republicans. A Bayes factor of .10 supported greater
probability for the equal use of \emph{ingroup} words with little
difference between Republicans (\emph{M} = 2.55, \emph{SD} = 2.83) and
Democrats (\emph{M} = 2.48, \emph{SD} = 2.10). A Bayes factor of .04
also supported greater likelihood of the equal use of \emph{authority}
words with no substantial difference between Republicans (\emph{M} =
3.06, \emph{SD} = 3.43) and Democrats (\emph{M} = 3.22, \emph{SD} =
3.19). Likewise, a Bayes factor of .09 demonstrated a greater
probability for the equal use of \emph{purity} words with little to no
difference between Republicans (\emph{M} = 1.52, \emph{SD} = 1.03) and
Democrats (\emph{M} = 1.54, \emph{SD} = 1.04). See \emph{figure ?} for
all comparisons.

\subsection{Discussion}\label{discussion}

\begin{verbatim}
The preceding analyses seem to suggest the MFD has limited validity. While the step procedure of the MTMM supports the assumptions that the MFD is measuring the same constructs as the MFQ, the models themselves suggest the MFD measures moral foundations rather poorly. Furthermore, the MFD fails to have the predictive validity found in the MFQ predicting political orientation. Based on the initial work of [@Graham2009], it is possible that the MFD is measuring the moral foundation constructs differently than the MFQ as they did find ingroup words to predict liberal orientation rather than conservative. The problems with the MFD may be due to the use of word frequency. As we found in the current study, the words of the MFD are not used very often which forced us to delete many participants and also left many participants who used only 2 or 3 words from the dictionary. The infrequent use of the MFD words may have caused some mismeasurement of the foundations. The LSA approach taken by @Sagi2013 may be a solution to this problem and may represent a better application of the dictionary. A limitation of the current study was word count for the texts, which could have exacerbated the word frequency problem. The average word count in our study was around 100-200 words; increasing the word count may yield better results in future studies. However, overall it seems that the word frequency method of the MFD is a poor measure of moral foundations theory. Further research is required to either improve the MFD or determine what exactly it is measuring. 
\end{verbatim}

\hypertarget{refs}{}
\hypertarget{ref-Federico2013}{}
Federico, C. M., Weber, C. R., Ergun, D., \& Hunt, C. (2013). Mapping
the Connections between Politics and Morality: The Multiple
Sociopolitical Orientations Involved in Moral Intuition. \emph{Political
Psychology}, \emph{34}(4), 589--610.
doi:\href{https://doi.org/10.1111/pops.12006}{10.1111/pops.12006}

\hypertarget{ref-Graham2009}{}
Graham, J., Haidt, J., \& Nosek, B. A. (2009). Liberals and
conservatives rely on different sets of moral foundations. \emph{Journal
of Personality and Social Psychology}, \emph{96}(5), 1029--1046.
doi:\href{https://doi.org/10.1037/a0015141}{10.1037/a0015141}

\hypertarget{ref-Graham2012}{}
Graham, J., Nosek, B. A., \& Haidt, J. (2012). The Moral Stereotypes of
Liberals and Conservatives: Exaggeration of Differences across the
Political Spectrum. \emph{PLoS ONE}, \emph{7}(12), e50092.
doi:\href{https://doi.org/10.1371/journal.pone.0050092}{10.1371/journal.pone.0050092}

\hypertarget{ref-Haidt2004}{}
Haidt, J., \& Joseph, C. (2004). Intuitive ethics: how innately prepared
intuitions generate culturally variable virtues. \emph{Daedalus},
\emph{133}(4), 55--66.
doi:\href{https://doi.org/10.1162/0011526042365555}{10.1162/0011526042365555}

\hypertarget{ref-Haidt2009}{}
Haidt, J., Graham, J., \& Joseph, C. (2009). Above and Below
Left--Right: Ideological Narratives and Moral Foundations.
\emph{Psychological Inquiry}, \emph{20}(2-3), 110--119.
doi:\href{https://doi.org/10.1080/10478400903028573}{10.1080/10478400903028573}

\hypertarget{ref-Kertzer2014}{}
Kertzer, J. D., Powers, K. E., Rathbun, B. C., \& Iyer, R. (2014). Moral
Support: How Moral Values Shape Foreign Policy Attitudes. \emph{The
Journal of Politics}, \emph{76}(3), 825--840.
doi:\href{https://doi.org/10.1017/S0022381614000073}{10.1017/S0022381614000073}

\hypertarget{ref-Koleva2012}{}
Koleva, S. P., Graham, J., Iyer, R., Ditto, P. H., \& Haidt, J. (2012).
Tracing the threads: How five moral concerns (especially Purity) help
explain culture war attitudes. \emph{Journal of Research in
Personality}, \emph{46}(2), 184--194.
doi:\href{https://doi.org/10.1016/j.jrp.2012.01.006}{10.1016/j.jrp.2012.01.006}

\hypertarget{ref-Weber2013}{}
Weber, C. R., \& Federico, C. M. (2013). Moral Foundations and
Heterogeneity in Ideological Preferences. \emph{Political Psychology},
\emph{34}(1), 107--126.
doi:\href{https://doi.org/10.1111/j.1467-9221.2012.00922.x}{10.1111/j.1467-9221.2012.00922.x}






\end{document}
