---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
#install.packages(c("devtools", "rio", "lavaan", "mice"))
#devtools::install_github("crsh/papaja")
library(papaja)
library(rio)
library(lavaan)
library(mice)

percentmiss <- function(x){ sum(is.na(x))/length(x) *100 }
```

# Section 1 Hypothesis 1 

- get new codings for the MFD (done!)
- MTMM of both together and show it's crappy 
  - exp2_finalsample_newMFD.csv is the data you want to use 
  - if step X of the mtmm - CFI > .50, TLI > .45, RSMEA < .50, SRMR < .50 - then keep going otherwise, stop
- CFA on the MFQ to determine if it works ok 

```{r import-exp2, include = F}
# Import the data
exp2 <- import("exp2_finalsample_newMFD.csv")

# Only use people with 25+ words
exp2 <- subset(exp2, WC >= 25)

# Data Screening for the MFQ

# Missing by rows 
missing <- apply(exp2[ , c(2:31)], 1, percentmiss)
goodrows <- subset(exp2, missing <= 5)
# Missing by columns
# table(round(missing,2))
# round(apply(goodrows, 2, percentmiss),2)

# Fix the missing MFQ
goodcolumns <- goodrows[ , c(1:31)]
badcolumns <- goodrows[ , c(31:ncol(goodrows))]

# Fill in missing data points
tempnomiss <- mice(goodcolumns)
nomiss <- complete(tempnomiss, 1)
nomiss <- cbind(nomiss, badcolumns) 

# Outliers
mahal <- mahalanobis(nomiss[ , c(2:31)],
                     colMeans(nomiss[ , c(2:31)], na.rm = T),
                     cov(nomiss[ , c(2:31)], use = "pairwise.complete.obs"))
cutoff <- qchisq(1 - .001, ncol(nomiss[ , c(2:31)]))
summary(mahal < cutoff) 
noout <- subset(nomiss, mahal < cutoff)

# Additivity
correlations <- cor(noout[ , c(2:31)], use = "pairwise.complete.obs")
# symnum(correlations)

# Started assumptions
random <- rchisq(nrow(noout), 7)
fake <- lm(random ~ ., data = noout[ , c(2:31)])

# Normal
standardized <- rstudent(fake)
hist(standardized, breaks = 15)

# Linear
{qqnorm(standardized); abline(0,1)}

# Homog + s
fitvalues <- scale(fake$fitted.values)
{plot(fitvalues, standardized); abline(0,0); abline(v = 0)}

# Create subscales
noout$harmMFQ <- apply(noout[ , 2:4], 1, sum)
noout$fairMFQ <- apply(noout[ , 5:7], 1, sum)
noout$ingroupMFQ <- apply(noout[ , 8:10], 1, sum)
noout$authorityMFQ <- apply(noout[ , 11:13], 1, sum)
noout$purityMFQ <- apply(noout[ , 14:16], 1, sum)
```

```{r cfa-mfq, include = F}
model <- "
harm =~ Q8_1 + Q8_2 + Q8_3
fair =~ Q8_4 + Q8_5 + Q8_6
ingroup =~ Q8_7 + Q8_8 + Q8_9
authority =~ Q8_10 + Q8_11 + Q8_12
purity =~ Q8_13 + Q8_14 + Q8_15
"

model.fit <- cfa(model = model,
                 data = noout)

summary(model.fit,
        standardized = T,
        rsquare = T,
        fit.measures = T)
```

- Only real thing I notice is the high intercorrelation of the latent variables for a few of them. 

```{r mtmm-model1, include = F}
# Correlated traits and methods
model1 <- "harmL =~ Q8_1 + Q8_2 + Q8_3 + Harm1
fairL =~ Q8_4 + Q8_5 + Q8_6 + Fairness1
ingroupL =~ Q8_7 + Q8_8 + Q8_9 + Loyalty1
authorityL =~ Q8_10 + Q8_11 + Q8_12 + Authority1
purityL=~ Q8_13 + Q8_14 + Q8_15 + Purity1 
mfq =~ Q8_1 + Q8_2 + Q8_3 + Q8_4 + Q8_5 + Q8_6 + Q8_7 + Q8_8 + Q8_9 + Q8_10 + Q8_11 + Q8_12 + Q8_13 + Q8_14 + Q8_15
mfd =~ Harm1 + Fairness1 + Loyalty1 + Authority1 + Purity1

# Fix the covariances
harmL ~~ 0*mfq
fairL ~~ 0*mfq
ingroupL ~~ 0*mfq
authorityL ~~ 0*mfq
purityL ~~ 0*mfq
harmL ~~ 0*mfd
fairL ~~ 0*mfd
ingroupL ~~ 0*mfd
authorityL ~~ 0*mfd
purityL ~~ 0*mfd
"

model1.fit <- cfa(model = model1, 
                  data = noout, 
                  std.lv=TRUE)

summary(model1.fit,
        rsquare = T,
        standardized = T,
        fit.measures = T)
```

```{r mtmm-model2, include = F}
# No traits, correlated methods
model2 <- "
mfq =~ Q8_1 + Q8_2 + Q8_3 + Q8_4 + Q8_5 + Q8_6 + Q8_7 + Q8_8 + Q8_9 + Q8_10 + Q8_11 + Q8_12 + Q8_13 + Q8_14 + Q8_15
mfd =~ Harm1 + Fairness1 + Loyalty1 + Authority1 + Purity1
"

model2.fit <- cfa(model = model2, 
                  data = noout, 
                  std.lv=TRUE)

summary(model2.fit,
        rsquare = T,
        standardized = T,
        fit.measures = T)
```

```{r mtmm-model3, include = F}
# Perfectly correlated traits, correlated methods
model3 <- "
harmL =~ Q8_1 + Q8_2 + Q8_3 + Harm1
fairL =~ Q8_4 + Q8_5 + Q8_6 + Fairness1
ingroupL =~ Q8_7 + Q8_8 + Q8_9 + Loyalty1
authorityL =~ Q8_10 + Q8_11 + Q8_12 + Authority1
purityL=~ Q8_13 + Q8_14 + Q8_15 + Purity1 
mfq =~ Q8_1 + Q8_2 + Q8_3 + Q8_4 + Q8_5 + Q8_6 + Q8_7 + Q8_8 + Q8_9 + Q8_10 + Q8_11 + Q8_12 + Q8_13 + Q8_14 + Q8_15
mfd =~ Harm1 + Fairness1 + Loyalty1 + Authority1 + Purity1

# Fix the covariances
harmL ~~ 0*mfq
fairL ~~ 0*mfq
ingroupL ~~ 0*mfq
authorityL ~~ 0*mfq
purityL ~~ 0*mfq
harmL ~~ 0*mfd
fairL ~~ 0*mfd
ingroupL ~~ 0*mfd
authorityL ~~ 0*mfd
purityL ~~ 0*mfd

# Correlate traits
harmL~~1*fairL
harmL~~1*ingroupL
harmL~~1*authorityL
harmL~~1*purityL
fairL~~1*ingroupL
fairL~~1*authorityL
fairL~~1*purityL
ingroupL~~1*authorityL
ingroupL~~1*purityL
authorityL~~1*purityL
"

model3.fit <- cfa(model = model3, 
                  data = noout, 
                  std.lv=TRUE)

summary(model3.fit,
        rsquare = T,
        standardized = T,
        fit.measures = T)
```

```{r mtmm-model4, include = F}
# Correlated traits, uncorrelated methods
model4 <- "harmL =~ Q8_1 + Q8_2 + Q8_3 + Harm1
fairL =~ Q8_4 + Q8_5 + Q8_6 + Fairness1
ingroupL =~ Q8_7 + Q8_8 + Q8_9 + Loyalty1
authorityL =~ Q8_10 + Q8_11 + Q8_12 + Authority1
purityL=~ Q8_13 + Q8_14 + Q8_15 + Purity1 
mfq =~ Q8_1 + Q8_2 + Q8_3 + Q8_4 + Q8_5 + Q8_6 + Q8_7 + Q8_8 + Q8_9 + Q8_10 + Q8_11 + Q8_12 + Q8_13 + Q8_14 + Q8_15
mfd =~ Harm1 + Fairness1 + Loyalty1 + Authority1 + Purity1

# Fix the covariances
harmL ~~ 0*mfq
fairL ~~ 0*mfq
ingroupL ~~ 0*mfq
authorityL ~~ 0*mfq
purityL ~~ 0*mfq
harmL ~~ 0*mfd
fairL ~~ 0*mfd
ingroupL ~~ 0*mfd
authorityL ~~ 0*mfd
purityL ~~ 0*mfd

# No method correlation
mfq ~~ 0*mfd
"

model4.fit <- cfa(model = model4, 
                  data = noout, 
                  std.lv=TRUE)

summary(model4.fit,
        rsquare = T,
        standardized = T,
        fit.measures = T)
```

```{r compare-models, include = F}
anova(model1.fit, model2.fit, model3.fit, model4.fit)
fitmeasures(model1.fit, "cfi")
fitmeasures(model2.fit, "cfi")
fitmeasures(model3.fit, "cfi")
fitmeasures(model4.fit, "cfi")
```

# Section 2

study 2: free association + two free writing samples data to build a new dictionary, build something better like vector space model or word2vec or cluster to see what is being picked up in the writing

# Section 3

study 3: testing study 2 in the congressional dataset that may need some cleaning up





# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
